---
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

<!-- ioslides_presentation: default -->

# WWGV survey regression analysis (first wave)

This document investigates the effect of covariates on the responses given in the Camden vaccine survey using generalised linear regression. This aims to answer questions such as

> is a person more likely to have positive views about vaccinations if their demographics are $X$ and $Y$, where as those with $A$ and $B$ demographics are more likely to have negative views about vaccinations?

Ultimately, we want to be able to see if the data helps us do the following:

-   understand the differences in responses for different types of people which might help develop approaches to reach those people differently or focus particular messaging
-   e.g. white middle aged men don’t typically see campaigns, but get their information mostly from radio
-   and how we need to shape that messaging
-   e.g. Bangladeshi young women are worried about $X$ and $Y$, but not $A$

A lot of vaccination data is done by region (e.g. south east London) / borough or IMD and ethnicity so we can use those as the base categories that the data is split by.

We have taken binary valued outcomes from the survey and used with logistic regression.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-libraries, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(forcats)
library(effects)
library(ggeffects)
library(ggplot2)
library(sjPlot)
library(dotwhisker)
library(broom)
library(knitr)
library(kableExtra)
library(tidyr)
library(vaccineanalysis)
```

```{r select-questions-eval}
# which outcomes to include in analysis
eval_concerned      <- TRUE
eval_vacc_important <- TRUE
eval_vacc_eff       <- TRUE
eval_vacc_last_yr   <- FALSE
eval_vacc_next_yr   <- FALSE
eval_campaign_hear  <- FALSE
eval_mmr_doses      <- FALSE
```

## Data cleaning

The data are formatted with possible survey response as column headings and either selected or empty. We need to combine these columns in to a single covariate column.
We also clean and shorten text and convert to factors.

```{r load-data, message=FALSE, warning=FALSE}
vaccine_survey_raw <- readxl::read_xlsx(
  here::here("../data/SAV for LBON (Vaccine survey) 31 4.7.2025 - LABEL.xlsx"), sheet = "single-header")
```

```{r data-clean, message=FALSE, warning=FALSE}
data <- 
  process_survey_wave(
    survey_data = vaccine_survey_raw,
    output_path = here::here("../data_clean_wave1.RData")
  )
```

# Empirical analysis

This is equivalent to the data slice Excel workbook provided with the data. We create histograms of the raw data for each outcome question.

## Vaccinated last year

```{r vacc_last_yr-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_last_yr <- data |>
  dplyr::select(vacc_last_yr, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight) |> 
  dplyr::filter(vacc_last_yr != "Don't know/ can't recall") |> 
  dplyr::mutate(vacc_last_yr = fct_drop(vacc_last_yr),
                vacc_last_yr = as.numeric(vacc_last_yr) - 1)

last_yr_aggregate <- dat_last_yr |> 
  tidyr::pivot_longer(cols = c(-vacc_last_yr, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    vaccination_rate = weighted.mean(vacc_last_yr, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )

# plot

ggplot(last_yr_aggregate, aes(x = predictor_level, y = vaccination_rate, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(vaccination_rate * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Vaccinated next year

```{r vacc_next_yr-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_next_yr <- data |>
  dplyr::select(vacc_next_yr, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight) |> 
  dplyr::filter(vacc_next_yr != "Don't know/ unsure") %>%
  dplyr::mutate(vacc_next_yr = case_when(
    vacc_next_yr %in% c("Fairly likely", "Very likely") ~ 1,
    vacc_next_yr %in% c("Not at all likely", "Not very likely") ~ 0
  ))

next_yr_aggregate <- dat_next_yr |> 
  tidyr::pivot_longer(cols = c(-vacc_next_yr, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    vaccination_rate = weighted.mean(vacc_next_yr, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )

# plot

ggplot(next_yr_aggregate, aes(x = predictor_level, y = vaccination_rate, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(vaccination_rate * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```


## MMR doses

```{r mmr_doses-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_mmr <- data |>
  dplyr::select(mmr_doses, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight) |> 
  dplyr::filter(mmr_doses %in% 
                  c("Yes, I have", "No, I haven't")) |>
  dplyr::mutate(mmr_doses = fct_drop(mmr_doses),
                mmr_doses = as.numeric(mmr_doses) - 1)

mmr_aggregate <- dat_mmr |> 
  tidyr::pivot_longer(cols = c(-mmr_doses, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    p_mmr_doses = weighted.mean(mmr_doses, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )
  
# plot

ggplot(mmr_aggregate, aes(x = predictor_level, y = p_mmr_doses, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(p_mmr_doses * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Vaccine effective

```{r vacc_eff-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_vacc_eff <- data |>
  dplyr::select(vacc_eff, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight) |> 
  dplyr::filter(vacc_eff != "Neither agree nor disagree") |>
  dplyr::mutate(vacc_eff = case_when(
    vacc_eff %in% c("Strongly agree", "Tend to agree") ~ 1,
    vacc_eff %in% c("Strongly disagree", "Tend to disagree") ~ 0
  ))

vacc_eff_aggregate <- dat_vacc_eff |> 
  tidyr::pivot_longer(cols = c(-vacc_eff, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    p_vacc_eff = weighted.mean(vacc_eff, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )
  
# plot

ggplot(vacc_eff_aggregate, aes(x = predictor_level, y = p_vacc_eff, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(p_vacc_eff * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Concerned about negative side effects

```{r concerned-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_concerned <- data |>
  dplyr::select(concerned, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight) |> 
  dplyr::filter(concerned != "Neither agree nor disagree") |>
  dplyr::mutate(concerned = case_when(
    concerned %in% c("Strongly agree", "Tend to agree") ~ 1,
    concerned %in% c("Strongly disagree", "Tend to disagree") ~ 0
  ))

concern_aggregate <- dat_concerned |> 
  tidyr::pivot_longer(cols = c(-concerned, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    p_concerned = weighted.mean(concerned, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )
  
# plot

ggplot(concern_aggregate, aes(x = predictor_level, y = p_concerned, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(p_concerned * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Vaccines important

```{r vacc_imp-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
dat_vacc_imp <- data |>
  dplyr::select(vacc_important, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 
                'parent_guardian18',  # 'parent_guardian',
                'house_tenure',
                weight) |> 
  dplyr::filter(vacc_important != "Neither agree nor disagree") |>
  dplyr::mutate(vacc_important = case_when(
    vacc_important %in% c("Strongly agree", "Tend to agree") ~ 1,
    vacc_important %in% c("Strongly disagree", "Tend to disagree") ~ 0
  ))

vacc_imp_aggregate <- dat_vacc_imp |> 
  tidyr::pivot_longer(cols = c(-vacc_important, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    p_vacc_important = weighted.mean(vacc_important, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )

# plot

ggplot(vacc_imp_aggregate, aes(x = predictor_level, y = p_vacc_important, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(p_vacc_important * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Heard (positive) about campaign

```{r campaign_hear-histograms, message=FALSE, warning=FALSE, fig.height=10, fig.path="figures/", dev="png"}
# remove heard negative and then did they hear anything?
dat_hear <- data |>
  dplyr::mutate(campaign_hear = ifelse(is.na(`Not applicable - I've not heard anything about any of these campaigns`), 1, 0)) |> 
  dplyr::filter(!negative_hear %in% c("y", "selected")) |> 
  dplyr::select(campaign_hear, Age, Gender, 'social_grade', 'ethnicity_grp', 'marital_status', 'working_status',
                'children_in_household', 'parent_guardian', 'house_tenure',
                weight)

hear_aggregate <- dat_hear |> 
  tidyr::pivot_longer(cols = c(-campaign_hear, -weight), 
                      names_to = "predictor",
                      values_to = "predictor_level") |> 
  dplyr::group_by(predictor, predictor_level) |> 
  dplyr::summarise(
    p_campaign_hear = mean(campaign_hear, na.rm = TRUE),
    p_campaign_hear = weighted.mean(campaign_hear, w = weight, na.rm = TRUE),
    sample_size = n(),
    weighted_pop = sum(weight, na.rm = TRUE),
    .groups = "drop"
  )
  
# plot

ggplot(hear_aggregate, aes(x = predictor_level, y = p_campaign_hear, fill = predictor_level)) +
  geom_col() +  # for pre-summarised data
  geom_text(aes(label = paste0(round(p_campaign_hear * 100), "%")), vjust = -0.5) +
  facet_wrap(~ predictor, scales = "free_x") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

```{r save-sep-outcome-data, message=FALSE, warning=FALSE}
save(dat_last_yr, dat_next_yr, dat_mmr, dat_vacc_eff, dat_concerned, dat_vacc_imp, dat_hear,
     file = here::here("data/separate_outcome_data.RData"))
```


## Pairs comparison

A pairs scatter plot gives an idea of the relationship between pairs of outcomes.

```{r pairs-scatterplot-wave1, message=FALSE, warning=FALSE, eval=FALSE}
#
mmr_aggregate_dummy <- 
  rbind.data.frame(mmr_aggregate,
      list("parent_guardian", "Not parent/ guardian", 0, 0))

data.frame(last_yr_aggregate$vaccination_rate, 
           next_yr_aggregate$vaccination_rate, 
           concern_aggregate$p_concerned,
           hear_aggregate$p_campaign_hear,
           vacc_imp_aggregate$p_vacc_important,
           mmr_aggregate_dummy$p_mmr_doses) |> 
  GGally::ggpairs(columnLabels = c("Last year", "Next year", "Concerned", "Campaign hear", "Vacc important", "MMR doses"),
    lower = list(continuous = GGally::wrap("smooth", method = "lm", se = FALSE))
  )

ggsave(filename = "figures/pair-scatterplot.png")
```

# Regression analysis

Next we fit separate logistic regressions for each outcome question.
The covariates used are

1.  Age group
2.  Gender
3.  Social grade
4.  Ethnicity group
5.  Marital status
6.  Working status
7.  Number of children in household
8.  Parent or guardian dependency age group
9.  House tenure

## Vaccinated last year

```{r}
library(brms)
library(purrr)
library(marginaleffects)
library(forcats)

dat_last_yr$house_tenure <- fct_collapse(dat_last_yr$house_tenure,
  "Own" = c("Own outright", "Own with a mortgage", "Shared ownership scheme"),
  "Missing" = "blank"
)
levels(dat_last_yr$marital_status)[levels(dat_last_yr$marital_status) == "blank"] <- "Missing"
library(rstanarm)
fit_rstanarm <- rstanarm::stan_glm(
  vacc_last_yr ~ Age + Gender + social_grade + ethnicity_grp +
    marital_status + house_tenure + working_status +
    parent_guardian + children_in_household,
  
  data = dat_last_yr,#dat_last_yr_clean,
  family = binomial(link = "logit"),
  
  weights = weight,
  
  # prior = normal(location = 0, scale = 100, autoscale = FALSE),
  # prior_intercept = normal(location = 0, scale = 100, autoscale = FALSE),
  
  chains = 4,
  iter = 2000
)
#comparison of the observed with posterior predictive vac proportion
library(bayesplot)
y_rep <- posterior_predict(fit_rstanarm)
ppc_stat(y = dat_last_yr$vacc_last_yr, yrep = y_rep[1:4000, ], stat = "mean")


predictors <- c("Age", "Gender", "social_grade", "ethnicity_grp", 
                "marital_status", "house_tenure", "working_status", 
                "parent_guardian", "children_in_household")

eff_df_bayesian <- map_dfr(predictors, function(p) {
  
  # 1. Create the grid for this specific predictor
  nd <- dat_last_yr %>%
    modelr::data_grid(!!sym(p), .model = dat_last_yr)
  
  
  # 2. Get the draws on the probability scale
  post_probs <- posterior_epred(fit_rstanarm, newdata = nd, re_formula = NULL)
  
  # 3. Calculate the proportion of draws >= 0.5 for each level
  # colMeans on a logical comparison gives the probability (0 to 1)
  p_gt_50 <- colMeans(post_probs >= 0.5)
  lower_vals <- apply(post_probs, 2, quantile, probs = 0.025)
  upper_vals <- apply(post_probs, 2, quantile, probs = 0.975)
  # 4. Summary statistics
  nd %>%
    mutate(
      predictor = p,
      predictor_level = as.character(!!sym(p)),
      fit = colMeans(post_probs),
      lower = apply(post_probs, 2, quantile, probs = 0.025),
      upper = apply(post_probs, 2, quantile, probs = 0.975),
      # New column: 1 if more than half the posterior mass is >= 0.5, else 0
      # Or simply keep it as a continuous probability if you prefer
      #above_50_threshold = ifelse(p_gt_50 >= 0.5, 1, 0) 
      above_50_threshold = case_when(
        p_gt_50 < 0.5                       ~ 0,
        p_gt_50 >= 0.5 & lower_vals <= 0.5  ~ 1,
        p_gt_50 >= 0.5 & lower_vals > 0.5   ~ 2
      )
    ) %>%
    select(predictor, predictor_level, fit, lower, upper, above_50_threshold)
})

eff_df_bayesian <- eff_df_bayesian %>%
  mutate(threshold_group = case_when(
    above_50_threshold == 2 ~ "Above C.I. no overlap 50%",
    above_50_threshold == 1 ~ "Above C.I. overlap 50%",
    above_50_threshold == 0 ~ "Below C.I. overlap 50%"
  ))


# 1. Update your nice_names to include line breaks for the long ones
nice_names <- c(
  "Age" = "Age",
  "children_in_household" = "Children\nin Household",
  "ethnicity_grp" = "Ethnicity",
  "Gender" = "Gender",
  "house_tenure" = "Housing",
  "marital_status" = "Marital\nStatus",
  "parent_guardian" = "Parental\nStatus",
  "social_grade" = "Social\nGrade",
  "working_status" = "Work\nStatus"
)

# 2. Run the plot with the labeller
ggplot(eff_df_bayesian, aes(x = predictor_level, y = fit, color = threshold_group)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "blue", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  
  scale_color_manual(values = c("Above C.I. no overlap 50%" = "green", 
                                "Above C.I. overlap 50%" = "grey", 
                                "Below C.I. overlap 50%" = "red")) + 
  
  # Use the 'labeller' argument to map the raw names to your nice names
  facet_grid(~ predictor, 
             scales = "free_x", 
             space = "free_x", 
             labeller = as_labeller(nice_names)) + 
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_blank(),           
    strip.text = element_text(face = "bold", size = 11, lineheight = 0.9), 
    panel.spacing = unit(0.5, "lines") # Increased slightly from 0 to avoid text overlap
  ) +
  labs(
    y = "Probability vaccinated last year",
    x = "Predictor Level",
    color = "Probability Threshold",
    title = "Posterior Predictive Probabilities"
  )
```


```{r vacc_last_yr_table, message=FALSE, warning=FALSE}
library(broom.mixed)
broom.mixed::tidy(fit_rstanarm, conf.int = TRUE) |> 
  kable(digits = 3, caption = "Logistic Regression Results") |> 
  kable_styling(full_width = FALSE)


library(rstanarm)
library(broom.mixed)
library(knitr)
library(kableExtra)
tab_latex <- broom.mixed::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  conf.level = 0.95,
  conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)

latex_table <- kable(
  tab_latex,
  format = "latex",
  booktabs = TRUE,
  digits = 3,
  caption = "Bayesian Logistic Regression Results (Odds Ratios, 95\\% Credible Intervals)",
  label = "tab:bayes_logit"
)

cat(latex_table)

```

```{r}

plot_labels <- c(
  "25-34",
  "35-44",
  "45-54", 
  "≥55",
  "Male",
  "Low",
  "Asian",
  "Black",
  "Mixed",
  "Other",
  "Prefer not to say",
  "Living as married",
  "Never Married",
  "Separated/ Divorced",
  "Widowed",
  "Missing",
  "Rent-free" = "house_tenureRent-free",
  "Rent from a housing association",
  "Rent from a private landlord",
  "Rent from my local authority",
  "Family/ friends but pay rent",
  "Other",
  "Missing",
  "Working part-time",
  "Full-time student",
  "Not working/ Other",
  "Retired",
  "Unemployed",
  "5 to 11 years",
  "12 to 16 years",
  "17 to 18 years",
  "Over 18 years",
  "Not parent/ guardian",
  "1",
  "2",
  "≥3",
  "Refused"
)

plot_labels <- c(
  "Age (ref: 18-24)" = "header_age",
  "   25-34" = "Age25-34",
  "   35-44" = "Age35-44",
  "   45-54" = "Age45-54",
  "   ≥ 55" = "Age55+",
  "Gender (ref: Female)" = "header_gender",
  "   Male" = "GenderMale",
  "Social Grade (ref: High)" = "header_social",
  "   Low" = "social_gradeLow",
  "Ethnicity (ref: White)" = "header_eth",
  "   Asian" = "ethnicity_grpAsian",
  "   Black" = "ethnicity_grpBlack",
  "   Mixed" = "ethnicity_grpMixed",
  "   Other" = "ethnicity_grpOther",
  "   Prefer not to say" = "ethnicity_grpPrefer not to say",
  "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
  "   Living as married" = "marital_statusLiving as married",
  "   Never Married" = "marital_statusNever Married",
  "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
  "   Widowed" = "marital_statusWidowed",
  "   Missing" = "marital_statusMissing",
  "Housing Tenure (ref: Own)" = "header_housing",
  "   Rent-free" = "house_tenureRent-free",
  "   Rent from a housing association" = "house_tenureRent from a housing association",
  "   Rent from a private landlord" = "house_tenureRent from a private landlord",
  "   Rent from my local authority" = "house_tenureRent from my local authority",
  "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
  "   Other" = "house_tenureOther",
  "   Missing" = "house_tenureMissing",
  "Working Status (ref: Working full time)" = "header_work",
  "   Working part-time" = "working_statusWorking part time",
  "   Full-time student" = "working_statusFull time student",
  "   Not working/ Other" = "working_statusNot working/ Other",
  "   Retired" = "working_statusRetired",
  "   Unemployed" = "working_statusUnemployed",
  "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
  "   5 to 11 years" = "parent_guardian5 to 11 years",
  "   12 to 16 years" = "parent_guardian12 to 16 years",
  "   17 to 18 years" = "parent_guardian17 to 18 years",
  "   Over 18 years" = "parent_guardianOver 18 years",
  "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
  "Number of Children in Household (ref: 0)" = "header_children",
  "   1" = "children_in_household1",
  "   2" = "children_in_household2",
  "   ≥ 3" = "children_in_household3+",
  "   Refused" = "children_in_householdRefused"
)

plot_labels_rev <- setNames(names(plot_labels), plot_labels)

```

```{r}


library(tidyverse)
library(broom.mixed)

# 1. Tidy the model
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = factor(term, levels = term)) %>%   # <-- LOCK ORDER
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age",
    str_detect(term, "Gender") ~ "Gender",
    str_detect(term, "social_grade") ~ "Social Grade",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity",
    str_detect(term, "marital_status") ~ "Marital Status",
    str_detect(term, "house_tenure") ~ "Housing Tenure",
    str_detect(term, "working_status") ~ "Working Status",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian",
    str_detect(term, "children_in_household") ~ "Number of Children in Household",
    TRUE ~ "Other"
  )) %>%
  # 3. STRICTLY ORDER THE GROUPS
  # We use fct_relevel to define the top-to-bottom order you requested
  mutate(group = fct_relevel(group, 
                             "Age", "Gender", "Social Grade", "Ethnicity", 
                             "Marital Status", "Housing Tenure", "Working Status", 
                             "Parent/Guardian", "Number of Children in Household")) %>%
  # 4. ORDER THE ROWS WITHIN THE GROUPS
  # We arrange by the group level, then by the estimate
  # Create the factor levels for 'term' based on this specific sorted order
  mutate(term = factor(term, levels = rev(unique(term)))) %>%
  mutate(color = ifelse(estimate > 1, "Increase", "Decrease"))




# 5. Forest plot
ggplot(posterior_df, aes(x = term, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "Predictors",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        legend.position = "none",
        panel.border = element_blank(),
    
    # 2. Add back only the Left (Y) and Bottom (X) lines
    axis.line = element_line(color = "black", linewidth = 0.5),
    #     axis.text.y = element_text(size = 10),
    # # Increase the size of the numbers on the bottom axis
    # axis.text.x = element_text(size = 10),
      aspect.ratio = 1.4,
    axis.text.y = element_text(size = 10, color = "black"),
    # Bold the Odds Ratio numbers (Bottom) - ONLY ONE INSTANCE HERE
    axis.text.x = element_text(size = 10,  color = "black"),
    axis.ticks = element_blank()        # Removes the little lines
    # Bold the Axis Titles
    # axis.title.x = element_text(face = "bold"),
    # axis.title.y = element_text(face = "bold")
 ) +
  scale_x_discrete(
  limits = rev(unname(plot_labels)),   # enforce full order including headers
  labels = plot_labels_rev
)

# +
#    scale_x_discrete(labels = c(plot_labels_rev
#  ))
```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Get the raw results from rstanarm
# Changed 'prob' to 'conf.level'
results <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE, conf.level = 0.95) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    # Approximate p-value from Z-score (Standard for academic tables)
    p.value = 2 * (1 - pnorm(abs(estimate / std.error))), 
    OR = sprintf("%.2f", estimate),
    CI = sprintf("%.2f, %.2f", conf.low, conf.high),
    P = case_when(
      p.value < 0.001 ~ "<0.001",
      p.value >= 0.99 ~ ">0.99",
      TRUE ~ sprintf("%.3f", p.value)
    )
  )


clean_table <- results %>%
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age (ref: 18-24)",
    str_detect(term, "Gender") ~ "Gender (ref: Female)",
    str_detect(term, "social_grade") ~ "Social Grade (ref: High)",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity (ref: White)",
    str_detect(term, "marital_status") ~ "Marital Status (ref: Married/ Civil Partnership)",
    str_detect(term, "house_tenure") ~ "Housing Tenure (ref: Own outright)",
    str_detect(term, "working_status") ~ "Working Status (ref: Working full time)",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian of Child Aged (ref: 4 years and under)",
    str_detect(term, "children_in_household") ~ "Children in Household (ref: 0)",
    TRUE ~ "Other"
  )) %>%
  # This regex removes the variable name prefix to leave just the level name
  mutate(level_name = str_remove(term, "Age|Gender|social_grade|ethnicity_grp|marital_status|house_tenure|working_status|parent_guardian|children_in_household"))

group_order <- c("Age (ref: 18-24)", "Gender (ref: Female)", "Social Grade (ref: High)", 
                 "Ethnicity (ref: White)", "Marital Status (ref: Married/ Civil Partnership)", 
                 "Housing Tenure (ref: Own outright)", "Working Status (ref: Working full time)", 
                 "Parent/Guardian of Child Aged (ref: 4 years and under)", "Children in Household (ref: 0)")

cat("% Copy the lines below into your LaTeX tabular environment\n")
for(g in group_order) {
  # Print the Header Row
  cat(paste0(g, " &  &  &  \\\\ \n"))
  cat("\\addlinespace[2.5pt]\n") # Adds the space you had in your template
  
  # Filter and print the indented sub-rows
  sub_grp <- clean_table %>% filter(group == g)
  
  if(nrow(sub_grp) > 0) {
    for(i in 1:nrow(sub_grp)) {
      # Use quadruple backslashes to result in two backslashes in the output
      cat(paste0("\\;\\;\\;\\;", sub_grp$level_name[i], " & ", 
                 sub_grp$OR[i], " & ", sub_grp$CI[i], " & ", sub_grp$P[i], " \\\\ \n"))
    }
  }
}

```


## Vaccinated next year

```{r vacc_next_yr-fits, fig.height=10, message=FALSE, warning=FALSE}
# idc_to_rem = unique(c(which(dat_next_yr$children_in_household == "Refused"),
# which(dat_next_yr$house_tenure == "blank"),
# which(dat_next_yr$marital_status == "blank")))
# dat_next_yr_clean = dat_next_yr[-idc_to_rem,]
# dat_next_yr_clean = dat_next_yr[-idc_to_rem,]
# dat_next_yr_clean$marital_status = fct_collapse(dat_next_yr_clean$marital_status, Widowed = c("Widowed", "blank"))
# dat_next_yr_clean$house_tenure = fct_collapse(dat_next_yr_clean$house_tenure, Other = c("Other", "blank"))
# dat_next_yr_clean$children_in_household = fct_collapse(dat_next_yr_clean$children_in_household, "3+" = c("3+", "Refused"))
dat_next_yr$house_tenure <- fct_collapse(dat_next_yr$house_tenure,
  "Own" = c("Own outright", "Own with a mortgage", "Shared ownership scheme"),
  "Missing" = "blank"
)
levels(dat_next_yr$marital_status)[levels(dat_next_yr$marital_status) == "blank"] <- "Missing"

fit_rstanarm <- rstanarm::stan_glm(
  vacc_next_yr ~ Age + Gender + social_grade + ethnicity_grp +
    marital_status + house_tenure + working_status +
    parent_guardian + children_in_household,
  
  data = dat_next_yr,
  family = binomial(link = "logit"),
  
  weights = weight,
  
  # prior = normal(location = 0, scale = 100, autoscale = FALSE),
  # prior_intercept = normal(location = 0, scale = 100, autoscale = FALSE),
  
  chains = 4,
  iter = 2000,
  seed = 123
)

y_rep <- posterior_predict(fit_rstanarm)
ppc_stat(y = dat_next_yr$vacc_next_yr, yrep = y_rep[1:4000, ], stat = "mean")


predictors <- c("Age", "Gender", "social_grade", "ethnicity_grp", 
                "marital_status", "house_tenure", "working_status", 
                "parent_guardian", "children_in_household")

eff_df_bayesian <- map_dfr(predictors, function(p) {
  
  # 1. Create the grid for this specific predictor
  nd <- dat_next_yr %>%
    modelr::data_grid(!!sym(p), .model = dat_next_yr)
  
  
  # 2. Get the draws on the probability scale
  post_probs <- posterior_epred(fit_rstanarm, newdata = nd, re_formula = NULL)
  
  # 3. Calculate the proportion of draws >= 0.5 for each level
  # colMeans on a logical comparison gives the probability (0 to 1)
  p_gt_50 <- colMeans(post_probs >= 0.5)
  lower_vals <- apply(post_probs, 2, quantile, probs = 0.025)
  upper_vals <- apply(post_probs, 2, quantile, probs = 0.975)
  # 4. Summary statistics
  nd %>%
    mutate(
      predictor = p,
      predictor_level = as.character(!!sym(p)),
      fit = colMeans(post_probs),
      lower = apply(post_probs, 2, quantile, probs = 0.025),
      upper = apply(post_probs, 2, quantile, probs = 0.975),
      # New column: 1 if more than half the posterior mass is >= 0.5, else 0
      # Or simply keep it as a continuous probability if you prefer
      #above_50_threshold = ifelse(p_gt_50 >= 0.5, 1, 0) 
      above_50_threshold = case_when(
        p_gt_50 < 0.5                       ~ 0,
        p_gt_50 >= 0.5 & lower_vals <= 0.5  ~ 1,
        p_gt_50 >= 0.5 & lower_vals > 0.5   ~ 2
      )
    ) %>%
    select(predictor, predictor_level, fit, lower, upper, above_50_threshold)
})

eff_df_bayesian <- eff_df_bayesian %>%
  mutate(threshold_group = case_when(
    above_50_threshold == 2 ~ "Above C.I. no overlap 50%",
    above_50_threshold == 1 ~ "Above C.I. overlap 50%",
    above_50_threshold == 0 ~ "Below C.I. overlap 50%"
  ))


# 1. Update your nice_names to include line breaks for the long ones
nice_names <- c(
  "Age" = "Age",
  "children_in_household" = "Children\nin Household",
  "ethnicity_grp" = "Ethnicity",
  "Gender" = "Gender",
  "house_tenure" = "Housing",
  "marital_status" = "Marital\nStatus",
  "parent_guardian" = "Parental\nStatus",
  "social_grade" = "Social\nGrade",
  "working_status" = "Work\nStatus"
)

# 2. Run the plot with the labeller
ggplot(eff_df_bayesian, aes(x = predictor_level, y = fit, color = threshold_group)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "blue", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  
  scale_color_manual(values = c("Above C.I. no overlap 50%" = "green", 
                                "Above C.I. overlap 50%" = "grey", 
                                "Below C.I. overlap 50%" = "red")) + 
  
  # Use the 'labeller' argument to map the raw names to your nice names
  facet_grid(~ predictor, 
             scales = "free_x", 
             space = "free_x", 
             labeller = as_labeller(nice_names)) + 
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_blank(),           
    strip.text = element_text(face = "bold", size = 11, lineheight = 0.9), 
    panel.spacing = unit(0.5, "lines") # Increased slightly from 0 to avoid text overlap
  ) +
  labs(
    y = "Probability vaccinated next year",
    x = "Predictor Level",
    color = "Probability Threshold",
    title = "Posterior Predictive Probabilities"
  )
```

```{r vacc_next_yr_table, message=FALSE, warning=FALSE}
broom::tidy(fit_rstanarm, conf.int = TRUE) |> 
  kable(digits = 3, caption = "Logistic Regression Results") %>%
  kable_styling(full_width = FALSE)



library(rstanarm)
library(broom.mixed)
library(knitr)
library(kableExtra)
tab_latex <- broom.mixed::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  conf.level = 0.95,
  conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)

tab_latex <- broom::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  # conf.level = 0.95,
  # conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)


latex_table <- kable(
  tab_latex,
  format = "latex",
  booktabs = TRUE,
  digits = 3,
  caption = "Bayesian Logistic Regression Results (Odds Ratios, 95\\% Credible Intervals)",
  label = "tab:bayes_logit"
)

cat(latex_table)

```


```{r}

plot_labels <- c(
  "25-34",
  "35-44",
  "45-54", 
  "≥55",
  "Male",
  "Low",
  "Asian",
  "Black",
  "Mixed",
  "Other",
  "Prefer not to say",
  "Living as married",
  "Never Married",
  "Separated/ Divorced",
  "Widowed",
  "Missing",
  "Rent-free" = "house_tenureRent-free",
  "Rent from a housing association",
  "Rent from a private landlord",
  "Rent from my local authority",
  "Family/ friends but pay rent",
  "Other",
  "Missing",
  "Working part-time",
  "Full-time student",
  "Not working/ Other",
  "Retired",
  "Unemployed",
  "5 to 11 years",
  "12 to 16 years",
  "17 to 18 years",
  "Over 18 years",
  "Not parent/ guardian",
  "1",
  "2",
  "≥3",
  "Refused"
)

plot_labels <- c(
  "Age (ref: 18-24)" = "header_age",
  "   25-34" = "Age25-34",
  "   35-44" = "Age35-44",
  "   45-54" = "Age45-54",
  "   ≥ 55" = "Age55+",
  "Gender (ref: Female)" = "header_gender",
  "   Male" = "GenderMale",
  "Social Grade (ref: High)" = "header_social",
  "   Low" = "social_gradeLow",
  "Ethnicity (ref: White)" = "header_eth",
  "   Asian" = "ethnicity_grpAsian",
  "   Black" = "ethnicity_grpBlack",
  "   Mixed" = "ethnicity_grpMixed",
  "   Other" = "ethnicity_grpOther",
  "   Prefer not to say" = "ethnicity_grpPrefer not to say",
  "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
  "   Living as married" = "marital_statusLiving as married",
  "   Never Married" = "marital_statusNever Married",
  "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
  "   Widowed" = "marital_statusWidowed",
  "   Missing" = "marital_statusMissing",
  "Housing Tenure (ref: Own)" = "header_housing",
  "   Rent-free" = "house_tenureRent-free",
  "   Rent from a housing association" = "house_tenureRent from a housing association",
  "   Rent from a private landlord" = "house_tenureRent from a private landlord",
  "   Rent from my local authority" = "house_tenureRent from my local authority",
  "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
  "   Other" = "house_tenureOther",
  "   Missing" = "house_tenureMissing",
  "Working Status (ref: Working full-time)" = "header_work",
  "   Working part-time" = "working_statusWorking part time",
  "   Full-time student" = "working_statusFull time student",
  "   Not working/ Other" = "working_statusNot working/ Other",
  "   Retired" = "working_statusRetired",
  "   Unemployed" = "working_statusUnemployed",
  "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
  "   5 to 11 years" = "parent_guardian5 to 11 years",
  "   12 to 16 years" = "parent_guardian12 to 16 years",
  "   17 to 18 years" = "parent_guardian17 to 18 years",
  "   Over 18 years" = "parent_guardianOver 18 years",
  "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
  "Number of Children in Household (ref: 0)" = "header_children",
  "   1" = "children_in_household1",
  "   2" = "children_in_household2",
  "   ≥ 3" = "children_in_household3+",
  "   Refused" = "children_in_householdRefused"
)

plot_labels_rev <- setNames(names(plot_labels), plot_labels)

```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Process data with manual ordering
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term != "(Intercept)") %>%
  
  # Create groups to define the order you requested
  mutate(group = case_when(
    str_detect(term, "Age") ~ 1,
    str_detect(term, "Gender") ~ 2,
    str_detect(term, "social_grade") ~ 3,
    str_detect(term, "ethnicity_grp") ~ 4,
    str_detect(term, "marital_status") ~ 5,
    str_detect(term, "house_tenure") ~ 6,
    str_detect(term, "working_status") ~ 7,
    str_detect(term, "parent_guardian") ~ 8,
    str_detect(term, "children_in_household") ~ 9,
    TRUE ~ 10
  )) %>%
  # Arrange by group first, then by the specific term
  arrange(group, term) %>%
  # Lock in the order for ggplot (reversed because of coord_flip)
  mutate(term_label = factor(term, levels = rev(unique(term))),
         color = ifelse(estimate > 1, "Increase", "Decrease"))

# 2. Forest plot
ggplot(posterior_df, aes(x = term_label, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_minimal(base_size = 14)

```




```{r}
library(tidyverse)
library(broom.mixed)

# 1. Get the raw results from rstanarm
# Changed 'prob' to 'conf.level'
results <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE, conf.level = 0.95) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    # Approximate p-value from Z-score (Standard for academic tables)
    p.value = 2 * (1 - pnorm(abs(estimate / std.error))), 
    OR = sprintf("%.2f", estimate),
    CI = sprintf("%.2f, %.2f", conf.low, conf.high),
    P = case_when(
      p.value < 0.001 ~ "<0.001",
      p.value >= 0.99 ~ ">0.99",
      TRUE ~ sprintf("%.3f", p.value)
    )
  )


clean_table <- results %>%
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age (ref: 18-24)",
    str_detect(term, "Gender") ~ "Gender (ref: Female)",
    str_detect(term, "social_grade") ~ "Social Grade (ref: High)",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity (ref: White)",
    str_detect(term, "marital_status") ~ "Marital Status (ref: Married/ Civil Partnership)",
    str_detect(term, "house_tenure") ~ "Housing Tenure (ref: Own outright)",
    str_detect(term, "working_status") ~ "Working Status (ref: Working full-time)",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian of Child Aged (ref: 4 years and under)",
    str_detect(term, "children_in_household") ~ "Number of Children in Household (ref: 0)",
    TRUE ~ "Other"
  )) %>%
  # This regex removes the variable name prefix to leave just the level name
  mutate(level_name = str_remove(term, "Age|Gender|social_grade|ethnicity_grp|marital_status|house_tenure|working_status|parent_guardian|children_in_household"))

group_order <- c("Age (ref: 18-24)", "Gender (ref: Female)", "Social Grade (ref: High)", 
                 "Ethnicity (ref: White)", "Marital Status (ref: Married/ Civil Partnership)", 
                 "Housing Tenure (ref: Own outright)", "Working Status (ref: Working full-time)", 
                 "Parent/Guardian of Child Aged (ref: 4 years and under)", "Number of Children in Household (ref: 0)")

cat("% Copy the lines below into your LaTeX tabular environment\n")
for(g in group_order) {
  # Print the Header Row
  cat(paste0(g, " &  &  &  \\\\ \n"))
  cat("\\addlinespace[2.5pt]\n") # Adds the space you had in your template
  
  # Filter and print the indented sub-rows
  sub_grp <- clean_table %>% filter(group == g)
  
  if(nrow(sub_grp) > 0) {
    for(i in 1:nrow(sub_grp)) {
      # Use quadruple backslashes to result in two backslashes in the output
      cat(paste0("\\;\\;\\;\\;", sub_grp$level_name[i], " & ", 
                 sub_grp$OR[i], " & ", sub_grp$CI[i], " & ", sub_grp$P[i], " \\\\ \n"))
    }
  }
}

```


```{r}


library(tidyverse)
library(broom.mixed)

# 1. Tidy the model
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = factor(term, levels = term)) %>%   # <-- LOCK ORDER
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age",
    str_detect(term, "Gender") ~ "Gender",
    str_detect(term, "social_grade") ~ "Social Grade",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity",
    str_detect(term, "marital_status") ~ "Marital Status",
    str_detect(term, "house_tenure") ~ "Housing Tenure",
    str_detect(term, "working_status") ~ "Working Status",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian",
    str_detect(term, "children_in_household") ~ "Number of Children in Household",
    TRUE ~ "Other"
  )) %>%
  # 3. STRICTLY ORDER THE GROUPS
  # We use fct_relevel to define the top-to-bottom order you requested
  mutate(group = fct_relevel(group, 
                             "Age", "Gender", "Social Grade", "Ethnicity", 
                             "Marital Status", "Housing Tenure", "Working Status", 
                             "Parent/Guardian", "Number of Children in Household")) %>%
  # 4. ORDER THE ROWS WITHIN THE GROUPS
  # We arrange by the group level, then by the estimate
  # Create the factor levels for 'term' based on this specific sorted order
  mutate(term = factor(term, levels = rev(unique(term)))) %>%
  mutate(color = ifelse(estimate > 1, "Increase", "Decrease"))

# 5. Forest plot
ggplot(posterior_df, aes(x = term, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "Predictors",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
              legend.position = "none",
        panel.border = element_blank(),
    
    # 2. Add back only the Left (Y) and Bottom (X) lines
    axis.line = element_line(color = "black", linewidth = 0.5),
    #     axis.text.y = element_text(size = 10),
    # # Increase the size of the numbers on the bottom axis
    # axis.text.x = element_text(size = 10),
        aspect.ratio = 1.4,
    axis.ticks = element_blank(),
    axis.text.y = element_text(size = 10, color = "black"),
    # Bold the Odds Ratio numbers (Bottom) - ONLY ONE INSTANCE HERE
    axis.text.x = element_text(size = 10, color = "black"),
    # Bold the Axis Titles
    # axis.title.x = element_text(face = "bold"),
    # axis.title.y = element_text(face = "bold")
    )+
  scale_x_discrete(
  limits = rev(unname(plot_labels)),   # enforce full order including headers
  labels = plot_labels_rev
)
```



## MMR doses

```{r mmr_doses-fits, fig.height=10, message=FALSE, warning=FALSE}


# idc_to_rem = unique(c(which(dat_mmr$children_in_household == "Refused"),
# which(dat_mmr$house_tenure == "blank"),
# which(dat_mmr$marital_status == "blank")))
# dat_mmr_clean = dat_mmr[-idc_to_rem,]
# dat_mmr_clean = dat_mmr[-idc_to_rem,]
# dat_mmr_clean$marital_status = fct_collapse(dat_mmr_clean$marital_status, Widowed = c("Widowed", "blank"))
# dat_mmr_clean$house_tenure = fct_collapse(dat_mmr_clean$house_tenure, Other = c("Other", "blank"))
# dat_mmr_clean$children_in_household = fct_collapse(dat_mmr_clean$children_in_household, "3+" = c("3+", "Refused"))

 dat_mmr_clean = dat_mmr |>
  dplyr::filter(ethnicity_grp != "Other",              # separation
                marital_status != "blank") %>%
droplevels()
  
dat_mmr_clean$house_tenure <- fct_collapse(dat_mmr_clean$house_tenure,
  "Own" = c("Own outright", "Own with a mortgage", "Shared ownership scheme"),
  "Missing" = "blank"
)

fit_rstanarm <- stan_glm(
  mmr_doses ~ Age + Gender + social_grade + ethnicity_grp +
    marital_status + house_tenure + working_status +
    parent_guardian + children_in_household,
  
  data = dat_mmr_clean,
  family = binomial(link = "logit"),
    prior = normal(location = 0, scale = 1, autoscale = FALSE),
  weights = weight,
  
  # prior = normal(location = 0, scale = 100, autoscale = FALSE),
  # prior_intercept = normal(location = 0, scale = 100, autoscale = FALSE),
  
  chains = 4,
  iter = 2000,
  seed = 123
)


y_rep <- posterior_predict(fit_rstanarm)
ppc_stat(y = dat_mmr_clean$mmr_doses, yrep = y_rep[1:4000, ], stat = "mean")


predictors <- c("Age", "Gender", "social_grade", "ethnicity_grp", 
                "marital_status", "house_tenure", "working_status", 
                "parent_guardian", "children_in_household")

eff_df_bayesian <- map_dfr(predictors, function(p) {
  
  # 1. Create the grid for this specific predictor
  nd <- dat_mmr_clean %>%
    modelr::data_grid(!!sym(p), .model = dat_mmr_clean)
  
  
  # 2. Get the draws on the probability scale
  post_probs <- posterior_epred(fit_rstanarm, newdata = nd, re_formula = NULL)
  
  # 3. Calculate the proportion of draws >= 0.5 for each level
  # colMeans on a logical comparison gives the probability (0 to 1)
  p_gt_50 <- colMeans(post_probs >= 0.5)
  lower_vals <- apply(post_probs, 2, quantile, probs = 0.025)
  upper_vals <- apply(post_probs, 2, quantile, probs = 0.975)
  # 4. Summary statistics
  nd %>%
    mutate(
      predictor = p,
      predictor_level = as.character(!!sym(p)),
      fit = colMeans(post_probs),
      lower = apply(post_probs, 2, quantile, probs = 0.025),
      upper = apply(post_probs, 2, quantile, probs = 0.975),
      # New column: 1 if more than half the posterior mass is >= 0.5, else 0
      # Or simply keep it as a continuous probability if you prefer
      #above_50_threshold = ifelse(p_gt_50 >= 0.5, 1, 0) 
      above_50_threshold = case_when(
        p_gt_50 < 0.5                       ~ 0,
        p_gt_50 >= 0.5 & lower_vals <= 0.5  ~ 1,
        p_gt_50 >= 0.5 & lower_vals > 0.5   ~ 2
      )
    ) %>%
    select(predictor, predictor_level, fit, lower, upper, above_50_threshold)
})

eff_df_bayesian <- eff_df_bayesian %>%
  mutate(threshold_group = case_when(
    above_50_threshold == 2 ~ "Above C.I. no overlap 50%",
    above_50_threshold == 1 ~ "Above C.I. overlap 50%",
    above_50_threshold == 0 ~ "Below C.I. overlap 50%"
  ))


# 1. Update your nice_names to include line breaks for the long ones
nice_names <- c(
  "Age" = "Age",
  "children_in_household" = "Children\nin HH",
  "ethnicity_grp" = "Ethnicity",
  "Gender" = "Gender",
  "house_tenure" = "Housing",
  "marital_status" = "Marital\nStatus",
  "parent_guardian" = "Parental\nStatus",
  "social_grade" = "Social\nGrade",
  "working_status" = "Work\nStatus"
)

# 2. Run the plot with the labeller
ggplot(eff_df_bayesian, aes(x = predictor_level, y = fit, color = threshold_group)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "blue", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  
  scale_color_manual(values = c("Above C.I. no overlap 50%" = "green", 
                                "Above C.I. overlap 50%" = "grey", 
                                "Below C.I. overlap 50%" = "red")) + 
  
  # Use the 'labeller' argument to map the raw names to your nice names
  facet_grid(~ predictor, 
             scales = "free_x", 
             space = "free_x", 
             labeller = as_labeller(nice_names)) + 
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_blank(),           
    strip.text = element_text(face = "bold", size = 11, lineheight = 0.9), 
    panel.spacing = unit(0.5, "lines") # Increased slightly from 0 to avoid text overlap
  ) +
  labs(
    y = "Probability vaccinated MMR dose",
    x = "Predictor Level",
    color = "Probability Threshold",
    title = "Posterior Predictive Probabilities"
  )
```

```{r mmr_doses_table, message=FALSE, warning=FALSE}
broom::tidy(fit_rstanarm, conf.int = TRUE) |> 
  kable(digits = 3, caption = "Logistic Regression Results") %>%
  kable_styling(full_width = FALSE)


library(rstanarm)
library(broom.mixed)
library(knitr)
library(kableExtra)
tab_latex <- broom::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  # conf.level = 0.95,
  # conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)

latex_table <- kable(
  tab_latex,
  format = "latex",
  booktabs = TRUE,
  digits = 3,
  caption = "Bayesian Logistic Regression Results (Odds Ratios, 95\\% Credible Intervals)",
  label = "tab:bayes_logit"
)

cat(latex_table)


```




```{r}

library(tidyverse)
library(broom.mixed)

# 1. Process data with your specific categorical order
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term != "(Intercept)") %>%
  # Create a numeric index based on your requested order
  mutate(group_order = case_when(
    str_detect(term, "Age") ~ 1,
    str_detect(term, "Gender") ~ 2,
    str_detect(term, "social_grade") ~ 3,
    str_detect(term, "ethnicity_grp") ~ 4,
    str_detect(term, "marital_status") ~ 5,
    str_detect(term, "house_tenure") ~ 6,
    str_detect(term, "working_status") ~ 7,
    str_detect(term, "parent_guardian") ~ 8,
    str_detect(term, "children_in_household") ~ 9,
    TRUE ~ 10
  )) %>%
  # Arrange by the group order, then by the term itself
  arrange(group_order, term) %>%
  # Create the factor levels based on the arranged order
  # We use rev() because coord_flip plots the first level at the bottom
  mutate(term_label = factor(term, levels = rev(unique(term))),
         color = ifelse(estimate > 1, "Increase", "Decrease"))

# 2. Forest plot
ggplot(posterior_df, aes(x = term_label, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") + # Moved back for cleaner look
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_minimal(base_size = 14)
```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Get the raw results from rstanarm
# Changed 'prob' to 'conf.level'
results <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE, conf.level = 0.95) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    # Approximate p-value from Z-score (Standard for academic tables)
    p.value = 2 * (1 - pnorm(abs(estimate / std.error))), 
    OR = sprintf("%.2f", estimate),
    CI = sprintf("%.2f, %.2f", conf.low, conf.high),
    P = case_when(
      p.value < 0.001 ~ "<0.001",
      p.value >= 0.99 ~ ">0.99",
      TRUE ~ sprintf("%.3f", p.value)
    )
  )


clean_table <- results %>%
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age (ref: 18-24)",
    str_detect(term, "Gender") ~ "Gender (ref: Female)",
    str_detect(term, "social_grade") ~ "Social Grade (ref: High)",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity (ref: White)",
    str_detect(term, "marital_status") ~ "Marital Status (ref: Married/ Civil Partnership)",
    str_detect(term, "house_tenure") ~ "Housing Tenure (ref: Own)",
    str_detect(term, "working_status") ~ "Working Status (ref: Working full-time)",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian of Child Aged (ref: 4 years and under)",
    str_detect(term, "children_in_household") ~ "Number of Children in Household (ref: 0)",
    TRUE ~ "Other"
  )) %>%
  # This regex removes the variable name prefix to leave just the level name
  mutate(level_name = str_remove(term, "Age|Gender|social_grade|ethnicity_grp|marital_status|house_tenure|working_status|parent_guardian|children_in_household"))

group_order <- c("Age (ref: 18-24)", "Gender (ref: Female)", "Social Grade (ref: High)", 
                 "Ethnicity (ref: White)", "Marital Status (ref: Married/ Civil Partnership)", 
                 "Housing Tenure (ref: Own)", "Working Status (ref: Working full-time)", 
                 "Parent/Guardian of Child Aged (ref: 4 years and under)", "Number of Children in Household (ref: 0)")

cat("% Copy the lines below into your LaTeX tabular environment\n")
for(g in group_order) {
  # Print the Header Row
  cat(paste0(g, " &  &  &  \\\\ \n"))
  cat("\\addlinespace[2.5pt]\n") # Adds the space you had in your template
  
  # Filter and print the indented sub-rows
  sub_grp <- clean_table %>% filter(group == g)
  
  if(nrow(sub_grp) > 0) {
    for(i in 1:nrow(sub_grp)) {
      # Use quadruple backslashes to result in two backslashes in the output
      cat(paste0("\\;\\;\\;\\;", sub_grp$level_name[i], " & ", 
                 sub_grp$OR[i], " & ", sub_grp$CI[i], " & ", sub_grp$P[i], " \\\\ \n"))
    }
  }
}

```


```{r}

plot_labels <- c(
  "25-34",
  "35-44",
  "45-54", 
  "≥55",
  "Male",
  "Low",
  "Asian",
  "Black",
  "Mixed",
  "Other",
  "Prefer not to say",
  "Living as married",
  "Never Married",
  "Separated/ Divorced",
  "Widowed",
  "Missing",
  "Rent-free" = "house_tenureRent-free",
  "Rent from a housing association",
  "Rent from a private landlord",
  "Rent from my local authority",
  "Family/ friends but pay rent",
  "Other",
  "Missing",
  "Working part-time",
  "Full-time student",
  "Not working/ Other",
  "Retired",
  "Unemployed",
  "5 to 11 years",
  "12 to 16 years",
  "17 to 18 years",
  "Over 18 years",
  "Not parent/ guardian",
  "1",
  "2",
  "≥3",
  "Refused"
)

plot_labels <- c(
  "Age (ref: 18-24)" = "header_age",
  "   25-34" = "Age25-34",
  "   35-44" = "Age35-44",
  "   45-54" = "Age45-54",
  "   ≥ 55" = "Age55+",
  "Gender (ref: Female)" = "header_gender",
  "   Male" = "GenderMale",
  "Social Grade (ref: High)" = "header_social",
  "   Low" = "social_gradeLow",
  "Ethnicity (ref: White)" = "header_eth",
  "   Asian" = "ethnicity_grpAsian",
  "   Black" = "ethnicity_grpBlack",
  "   Mixed" = "ethnicity_grpMixed",
  "   Other" = "ethnicity_grpOther",
  "   Prefer not to say" = "ethnicity_grpPrefer not to say",
  "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
  "   Living as married" = "marital_statusLiving as married",
  "   Never Married" = "marital_statusNever Married",
  "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
  "   Widowed" = "marital_statusWidowed",
  "   Missing" = "marital_statusMissing",
  "Housing Tenure (ref: Own)" = "header_housing",
  "   Rent-free" = "house_tenureRent-free",
  "   Rent from a housing association" = "house_tenureRent from a housing association",
  "   Rent from a private landlord" = "house_tenureRent from a private landlord",
  "   Rent from my local authority" = "house_tenureRent from my local authority",
  "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
  "   Other" = "house_tenureOther",
  "   Missing" = "house_tenureMissing",
  "Working Status (ref: Working full-time)" = "header_work",
  "   Working part-time" = "working_statusWorking part time",
  "   Full-time student" = "working_statusFull time student",
  "   Not working/ Other" = "working_statusNot working/ Other",
  "   Retired" = "working_statusRetired",
  "   Unemployed" = "working_statusUnemployed",
  "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
  "   5 to 11 years" = "parent_guardian5 to 11 years",
  "   12 to 16 years" = "parent_guardian12 to 16 years",
  "   17 to 18 years" = "parent_guardian17 to 18 years",
  "   Over 18 years" = "parent_guardianOver 18 years",
  "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
  "Number of Children in Household (ref: 0)" = "header_children",
  "   1" = "children_in_household1",
  "   2" = "children_in_household2",
  "   ≥ 3" = "children_in_household3+",
  "   Refused" = "children_in_householdRefused"
)

plot_labels_rev <- setNames(names(plot_labels), plot_labels)


# plot_labels <- c(
#   "25-34",
#   "35-44",
#   "45-54", 
#   "≥55",
#   "Male",
#   "Low",
#   "Asian",
#   "Black",
#   "Mixed",
#   "Other",
#   "Prefer not to say",
#   "Living as married",
#   "Never Married",
#   "Separated/ Divorced",
#   "Widowed",
#   "blank",
#   "Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "Rent-free" = "house_tenureRent-free",
#   "Rent from a housing association",
#   "Rent from a private landlord",
#   "Rent from my local authority",
#   "Family/ friends but pay rent",
#   "Shared ownership scheme",
#   "Other",
#   "blank",
#   "Working part time",
#   "Full time student",
#   "Not working/ Other",
#   "Retired",
#   "Unemployed",
#   "5 to 11 years",
#   "12 to 16 years",
#   "17 to 18 years",
#   "Over 18 years",
#   "Not parent/ guardian",
#   "1",
#   "2",
#   "≥3",
#   "Refused"
# )
# 
# plot_labels <- c(
#   "Age (ref: 18-24)" = "header_age",
#   "   25-34" = "Age25-34",
#   "   35-44" = "Age35-44",
#   "   45-54" = "Age45-54",
#   "   ≥ 55" = "Age55+",
#   "Gender (ref: Female)" = "header_gender",
#   "   Male" = "GenderMale",
#   "Social Grade (ref: High)" = "header_social",
#   "   Low" = "social_gradeLow",
#   "Ethnicity (ref: White)" = "header_eth",
#   "   Asian" = "ethnicity_grpAsian",
#   "   Black" = "ethnicity_grpBlack",
#   "   Mixed" = "ethnicity_grpMixed",
#   "   Other" = "ethnicity_grpOther",
#   "   Prefer not to say" = "ethnicity_grpPrefer not to say",
#   "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
#   "   Living as married" = "marital_statusLiving as married",
#   "   Never Married" = "marital_statusNever Married",
#   "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
#   "   Widowed" = "marital_statusWidowed",
#   "   blank" = "marital_statusblank",
#   "Housing Tenure (ref: Own outright)" = "header_housing",
#   "   Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "   Rent-free" = "house_tenureRent-free",
#   "   Rent from a housing association" = "house_tenureRent from a housing association",
#   "   Rent from a private landlord" = "house_tenureRent from a private landlord",
#   "   Rent from my local authority" = "house_tenureRent from my local authority",
#   "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
#   "   Shared ownership scheme" = "house_tenureShared ownership scheme",
#   "   Other" = "house_tenureOther",
#   "   blank" = "house_tenureblank",
#   "Working Status (ref: Working full time)" = "header_work",
#   "   Working part time" = "working_statusWorking part time",
#   "   Full time student" = "working_statusFull time student",
#   "   Not working/ Other" = "working_statusNot working/ Other",
#   "   Retired" = "working_statusRetired",
#   "   Unemployed" = "working_statusUnemployed",
#   "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
#   "   5 to 11 years" = "parent_guardian5 to 11 years",
#   "   12 to 16 years" = "parent_guardian12 to 16 years",
#   "   17 to 18 years" = "parent_guardian17 to 18 years",
#   "   Over 18 years" = "parent_guardianOver 18 years",
#   "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
#   "Children in Household (ref: 0)" = "header_children",
#   "   1" = "children_in_household1",
#   "   2" = "children_in_household2",
#   "   ≥ 3" = "children_in_household3+",
#   "   Refused" = "children_in_householdRefused"
# )
# 
# plot_labels_rev <- setNames(names(plot_labels), plot_labels)

```



```{r}


library(tidyverse)
library(broom.mixed)

# 1. Tidy the model
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = factor(term, levels = term)) %>%   # <-- LOCK ORDER
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age",
    str_detect(term, "Gender") ~ "Gender",
    str_detect(term, "social_grade") ~ "Social Grade",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity",
    str_detect(term, "marital_status") ~ "Marital Status",
    str_detect(term, "house_tenure") ~ "Housing Tenure",
    str_detect(term, "working_status") ~ "Working Status",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian",
    str_detect(term, "children_in_household") ~ "Number of Children in Household",
    TRUE ~ "Other"
  )) %>%
  # 3. STRICTLY ORDER THE GROUPS
  # We use fct_relevel to define the top-to-bottom order you requested
  mutate(group = fct_relevel(group, 
                             "Age", "Gender", "Social Grade", "Ethnicity", 
                             "Marital Status", "Housing Tenure", "Working Status", 
                             "Parent/Guardian", "Number of Children in Household")) %>%
  # 4. ORDER THE ROWS WITHIN THE GROUPS
  # We arrange by the group level, then by the estimate
  # Create the factor levels for 'term' based on this specific sorted order
  mutate(term = factor(term, levels = rev(unique(term)))) %>%
  mutate(color = ifelse(estimate > 1, "Increase", "Decrease"))

# 5. Forest plot
ggplot(posterior_df, aes(x = term, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "Predictors",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
         legend.position = "none",
        panel.border = element_blank(),
    
    # 2. Add back only the Left (Y) and Bottom (X) lines
    axis.line = element_line(color = "black", linewidth = 0.5),
    #     axis.text.y = element_text(size = 10),
    # # Increase the size of the numbers on the bottom axis
    # axis.text.x = element_text(size = 10),
         aspect.ratio = 1.4,
    axis.ticks = element_blank(),        # Removes the little lines
    axis.text.y = element_text(size = 10,  color = "black"),
    # Bold the Odds Ratio numbers (Bottom) - ONLY ONE INSTANCE HERE
    axis.text.x = element_text(size = 10,  color = "black"),
    # Bold the Axis Titles
    # axis.title.x = element_text(face = "bold"),
    # axis.title.y = element_text(face = "bold")
    )+
  scale_x_discrete(
  limits = rev(unname(plot_labels)),   # enforce full order including headers
  labels = plot_labels_rev
)
```




## Vaccine effective

```{r vacc_eff-fits, fig.height=10, message=FALSE, warning=FALSE}

 dat_vacc_eff_clean = dat_vacc_eff |> 
  dplyr::filter(ethnicity_grp != "Prefer not to say")%>%
droplevels()

dat_vacc_eff_clean$house_tenure <- fct_collapse(dat_vacc_eff_clean$house_tenure,
  "Own" = c("Own outright", "Own with a mortgage", "Shared ownership scheme"),
  "Missing" = "blank"
)
levels(dat_vacc_eff_clean$marital_status)[levels(dat_vacc_eff_clean$marital_status) == "blank"] <- "Missing"


fit_rstanarm <- stan_glm(
  vacc_eff ~ Age + Gender + social_grade + ethnicity_grp +
    marital_status + house_tenure + working_status +
    parent_guardian + children_in_household,
  
  data = dat_vacc_eff_clean,
  family = binomial(link = "logit"),
  
  
    prior = normal(location = 0, scale = 1, autoscale = FALSE),
  weights = weight,
  
  #prior = laplace(location = 0, scale = NULL, autoscale = TRUE),#normal(location = 0, scale = 10, autoscale = FALSE),
  # prior_intercept = normal(location = 0, scale = 10, autoscale = FALSE),
  
  chains = 4,
  iter = 2000,
  seed = 123
)

y_rep <- posterior_predict(fit_rstanarm)
ppc_stat(y = dat_vacc_eff_clean$vacc_eff, yrep = y_rep[1:4000, ], stat = "mean")


predictors <- c("Age", "Gender", "social_grade", "ethnicity_grp", 
                "marital_status", "house_tenure", "working_status", 
                "parent_guardian", "children_in_household")

eff_df_bayesian <- map_dfr(predictors, function(p) {
  
  # 1. Create the grid for this specific predictor
  nd <- dat_vacc_eff_clean %>%
    modelr::data_grid(!!sym(p), .model = dat_vacc_eff_clean)
  
  
  # 2. Get the draws on the probability scale
  post_probs <- posterior_epred(fit_rstanarm, newdata = nd, re_formula = NULL)
  
  # 3. Calculate the proportion of draws >= 0.5 for each level
  # colMeans on a logical comparison gives the probability (0 to 1)
  p_gt_50 <- colMeans(post_probs >= 0.5)
  lower_vals <- apply(post_probs, 2, quantile, probs = 0.025)
  upper_vals <- apply(post_probs, 2, quantile, probs = 0.975)
  # 4. Summary statistics
  nd %>%
    mutate(
      predictor = p,
      predictor_level = as.character(!!sym(p)),
      fit = colMeans(post_probs),
      lower = apply(post_probs, 2, quantile, probs = 0.025),
      upper = apply(post_probs, 2, quantile, probs = 0.975),
      # New column: 1 if more than half the posterior mass is >= 0.5, else 0
      # Or simply keep it as a continuous probability if you prefer
      #above_50_threshold = ifelse(p_gt_50 >= 0.5, 1, 0) 
      above_50_threshold = case_when(
        p_gt_50 < 0.5                       ~ 0,
        p_gt_50 >= 0.5 & lower_vals <= 0.5  ~ 1,
        p_gt_50 >= 0.5 & lower_vals > 0.5   ~ 2
      )
    ) %>%
    select(predictor, predictor_level, fit, lower, upper, above_50_threshold)
})

eff_df_bayesian <- eff_df_bayesian %>%
  mutate(threshold_group = case_when(
    above_50_threshold == 2 ~ "Above C.I. no overlap 50%",
    above_50_threshold == 1 ~ "Above C.I. overlap 50%",
    above_50_threshold == 0 ~ "Below C.I. overlap 50%"
  ))


# 1. Update your nice_names to include line breaks for the long ones
nice_names <- c(
  "Age" = "Age",
  "children_in_household" = "Children\nin HH",
  "ethnicity_grp" = "Ethnicity",
  "Gender" = "Gender",
  "house_tenure" = "Housing",
  "marital_status" = "Marital\nStatus",
  "parent_guardian" = "Parental\nStatus",
  "social_grade" = "Social\nGrade",
  "working_status" = "Work\nStatus"
)

# 2. Run the plot with the labeller
ggplot(eff_df_bayesian, aes(x = predictor_level, y = fit, color = threshold_group)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "blue", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  
  scale_color_manual(values = c("Above C.I. no overlap 50%" = "green", 
                                "Above C.I. overlap 50%" = "grey", 
                                "Below C.I. overlap 50%" = "red")) + 
  
  # Use the 'labeller' argument to map the raw names to your nice names
  facet_grid(~ predictor, 
             scales = "free_x", 
             space = "free_x", 
             labeller = as_labeller(nice_names)) + 
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_blank(),           
    strip.text = element_text(face = "bold", size = 11, lineheight = 0.9), 
    panel.spacing = unit(0.5, "lines") # Increased slightly from 0 to avoid text overlap
  ) +
  labs(
    y = "Probability vaccine effectiveness",
    x = "Predictor Level",
    color = "Probability Threshold",
    title = "Posterior Predictive Probabilities"
  )
```

```{r vacc_eff_table, message=FALSE, warning=FALSE}
broom::tidy(fit_rstanarm, conf.int = TRUE) |> 
  kable(digits = 3, caption = "Logistic Regression Results") %>%
  kable_styling(full_width = FALSE)


library(rstanarm)
library(broom.mixed)
library(knitr)
library(kableExtra)
tab_latex <- broom.mixed::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  conf.level = 0.95,
  conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)

latex_table <- kable(
  tab_latex,
  format = "latex",
  booktabs = TRUE,
  digits = 3,
  caption = "Bayesian Logistic Regression Results (Odds Ratios, 95\\% Credible Intervals)",
  label = "tab:bayes_logit"
)

cat(latex_table)


```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Process data with strict categorical ordering
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term != "(Intercept)") %>%
  # Define the categorical order you requested
  mutate(group_order = case_when(
    str_detect(term, "Age") ~ 1,
    str_detect(term, "Gender") ~ 2,
    str_detect(term, "social_grade") ~ 3,
    str_detect(term, "ethnicity_grp") ~ 4,
    str_detect(term, "marital_status") ~ 5,
    str_detect(term, "house_tenure") ~ 6,
    str_detect(term, "working_status") ~ 7,
    str_detect(term, "parent_guardian") ~ 8,
    str_detect(term, "children_in_household") ~ 9,
    TRUE ~ 10
  )) %>%
  # Arrange by the group order index
  arrange(group_order, term) %>%
  # Use rev() so the first group (Age) appears at the top after coord_flip()
  mutate(term_label = factor(term, levels = rev(unique(term))),
         color = ifelse(estimate > 1, "Increase", "Decrease"))

# 2. Forest plot
ggplot(posterior_df, aes(x = term_label, y = estimate, color = color)) +
  # Reference line at 1 for Odds Ratios
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_minimal(base_size = 14)
```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Get the raw results from rstanarm
# Changed 'prob' to 'conf.level'
results <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE, conf.level = 0.95) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    # Approximate p-value from Z-score (Standard for academic tables)
    p.value = 2 * (1 - pnorm(abs(estimate / std.error))), 
    OR = sprintf("%.2f", estimate),
    CI = sprintf("%.2f, %.2f", conf.low, conf.high),
    P = case_when(
      p.value < 0.001 ~ "<0.001",
      p.value >= 0.99 ~ ">0.99",
      TRUE ~ sprintf("%.3f", p.value)
    )
  )


clean_table <- results %>%
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age (ref: 18-24)",
    str_detect(term, "Gender") ~ "Gender (ref: Female)",
    str_detect(term, "social_grade") ~ "Social Grade (ref: High)",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity (ref: White)",
    str_detect(term, "marital_status") ~ "Marital Status (ref: Married/ Civil Partnership)",
    str_detect(term, "house_tenure") ~ "Housing Tenure (ref: Own)",
    str_detect(term, "working_status") ~ "Working Status (ref: Working full-time)",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian of Child Aged (ref: 4 years and under)",
    str_detect(term, "children_in_household") ~ "Number of Children in Household (ref: 0)",
    TRUE ~ "Other"
  )) %>%
  # This regex removes the variable name prefix to leave just the level name
  mutate(level_name = str_remove(term, "Age|Gender|social_grade|ethnicity_grp|marital_status|house_tenure|working_status|parent_guardian|children_in_household"))

group_order <- c("Age (ref: 18-24)", "Gender (ref: Female)", "Social Grade (ref: High)", 
                 "Ethnicity (ref: White)", "Marital Status (ref: Married/ Civil Partnership)", 
                 "Housing Tenure (ref: Own)", "Working Status (ref: Working full-time)", 
                 "Parent/Guardian of Child Aged (ref: 4 years and under)", "Number of Children in Household (ref: 0)")

cat("% Copy the lines below into your LaTeX tabular environment\n")
for(g in group_order) {
  # Print the Header Row
  cat(paste0(g, " &  &  &  \\\\ \n"))
  cat("\\addlinespace[2.5pt]\n") # Adds the space you had in your template
  
  # Filter and print the indented sub-rows
  sub_grp <- clean_table %>% filter(group == g)
  
  if(nrow(sub_grp) > 0) {
    for(i in 1:nrow(sub_grp)) {
      # Use quadruple backslashes to result in two backslashes in the output
      cat(paste0("\\;\\;\\;\\;", sub_grp$level_name[i], " & ", 
                 sub_grp$OR[i], " & ", sub_grp$CI[i], " & ", sub_grp$P[i], " \\\\ \n"))
    }
  }
}

```




```{r}

# plot_labels <- c(
#   "25-34",
#   "35-44",
#   "45-54", 
#   "≥55",
#   "Male",
#   "Low",
#   "Asian",
#   "Black",
#   "Mixed",
#   "Other",
#   "Prefer not to say",
#   "Living as married",
#   "Never Married",
#   "Separated/ Divorced",
#   "Widowed",
#   "blank",
#   "Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "Rent-free" = "house_tenureRent-free",
#   "Rent from a housing association",
#   "Rent from a private landlord",
#   "Rent from my local authority",
#   "Family/ friends but pay rent",
#   "Shared ownership scheme",
#   "Other",
#   "blank",
#   "Working part time",
#   "Full time student",
#   "Not working/ Other",
#   "Retired",
#   "Unemployed",
#   "5 to 11 years",
#   "12 to 16 years",
#   "17 to 18 years",
#   "Over 18 years",
#   "Not parent/ guardian",
#   "1",
#   "2",
#   "≥3",
#   "Refused"
# )
# 
# plot_labels <- c(
#   "Age (ref: 18-24)" = "header_age",
#   "   25-34" = "Age25-34",
#   "   35-44" = "Age35-44",
#   "   45-54" = "Age45-54",
#   "   ≥ 55" = "Age55+",
#   "Gender (ref: Female)" = "header_gender",
#   "   Male" = "GenderMale",
#   "Social Grade (ref: High)" = "header_social",
#   "   Low" = "social_gradeLow",
#   "Ethnicity (ref: White)" = "header_eth",
#   "   Asian" = "ethnicity_grpAsian",
#   "   Black" = "ethnicity_grpBlack",
#   "   Mixed" = "ethnicity_grpMixed",
#   "   Other" = "ethnicity_grpOther",
#   "   Prefer not to say" = "ethnicity_grpPrefer not to say",
#   "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
#   "   Living as married" = "marital_statusLiving as married",
#   "   Never Married" = "marital_statusNever Married",
#   "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
#   "   Widowed" = "marital_statusWidowed",
#   "   blank" = "marital_statusblank",
#   "Housing Tenure (ref: Own outright)" = "header_housing",
#   "   Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "   Rent-free" = "house_tenureRent-free",
#   "   Rent from a housing association" = "house_tenureRent from a housing association",
#   "   Rent from a private landlord" = "house_tenureRent from a private landlord",
#   "   Rent from my local authority" = "house_tenureRent from my local authority",
#   "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
#   "   Shared ownership scheme" = "house_tenureShared ownership scheme",
#   "   Other" = "house_tenureOther",
#   "   blank" = "house_tenureblank",
#   "Working Status (ref: Working full time)" = "header_work",
#   "   Working part time" = "working_statusWorking part time",
#   "   Full time student" = "working_statusFull time student",
#   "   Not working/ Other" = "working_statusNot working/ Other",
#   "   Retired" = "working_statusRetired",
#   "   Unemployed" = "working_statusUnemployed",
#   "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
#   "   5 to 11 years" = "parent_guardian5 to 11 years",
#   "   12 to 16 years" = "parent_guardian12 to 16 years",
#   "   17 to 18 years" = "parent_guardian17 to 18 years",
#   "   Over 18 years" = "parent_guardianOver 18 years",
#   "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
#   "Children in Household (ref: 0)" = "header_children",
#   "   1" = "children_in_household1",
#   "   2" = "children_in_household2",
#   "   ≥ 3" = "children_in_household3+",
#   "   Refused" = "children_in_householdRefused"
# )
# 
# plot_labels_rev <- setNames(names(plot_labels), plot_labels)

plot_labels <- c(
  "25-34",
  "35-44",
  "45-54", 
  "≥55",
  "Male",
  "Low",
  "Asian",
  "Black",
  "Mixed",
  "Other",
  "Prefer not to say",
  "Living as married",
  "Never Married",
  "Separated/ Divorced",
  "Widowed",
  "Missing",
  "Rent-free" = "house_tenureRent-free",
  "Rent from a housing association",
  "Rent from a private landlord",
  "Rent from my local authority",
  "Family/ friends but pay rent",
  "Other",
  "Missing",
  "Working part-time",
  "Full-time student",
  "Not working/ Other",
  "Retired",
  "Unemployed",
  "5 to 11 years",
  "12 to 16 years",
  "17 to 18 years",
  "Over 18 years",
  "Not parent/ guardian",
  "1",
  "2",
  "≥3",
  "Refused"
)

plot_labels <- c(
  "Age (ref: 18-24)" = "header_age",
  "   25-34" = "Age25-34",
  "   35-44" = "Age35-44",
  "   45-54" = "Age45-54",
  "   ≥ 55" = "Age55+",
  "Gender (ref: Female)" = "header_gender",
  "   Male" = "GenderMale",
  "Social Grade (ref: High)" = "header_social",
  "   Low" = "social_gradeLow",
  "Ethnicity (ref: White)" = "header_eth",
  "   Asian" = "ethnicity_grpAsian",
  "   Black" = "ethnicity_grpBlack",
  "   Mixed" = "ethnicity_grpMixed",
  "   Other" = "ethnicity_grpOther",
  "   Prefer not to say" = "ethnicity_grpPrefer not to say",
  "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
  "   Living as married" = "marital_statusLiving as married",
  "   Never Married" = "marital_statusNever Married",
  "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
  "   Widowed" = "marital_statusWidowed",
  "   Missing" = "marital_statusMissing",
  "Housing Tenure (ref: Own)" = "header_housing",
  "   Rent-free" = "house_tenureRent-free",
  "   Rent from a housing association" = "house_tenureRent from a housing association",
  "   Rent from a private landlord" = "house_tenureRent from a private landlord",
  "   Rent from my local authority" = "house_tenureRent from my local authority",
  "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
  "   Other" = "house_tenureOther",
  "   Missing" = "house_tenureMissing",
  "Working Status (ref: Working full-time)" = "header_work",
  "   Working part-time" = "working_statusWorking part time",
  "   Full-time student" = "working_statusFull time student",
  "   Not working/ Other" = "working_statusNot working/ Other",
  "   Retired" = "working_statusRetired",
  "   Unemployed" = "working_statusUnemployed",
  "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
  "   5 to 11 years" = "parent_guardian5 to 11 years",
  "   12 to 16 years" = "parent_guardian12 to 16 years",
  "   17 to 18 years" = "parent_guardian17 to 18 years",
  "   Over 18 years" = "parent_guardianOver 18 years",
  "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
  "Number of Children in Household (ref: 0)" = "header_children",
  "   1" = "children_in_household1",
  "   2" = "children_in_household2",
  "   ≥ 3" = "children_in_household3+",
  "   Refused" = "children_in_householdRefused"
)

plot_labels_rev <- setNames(names(plot_labels), plot_labels)



```

```{r}


library(tidyverse)
library(broom.mixed)

# 1. Tidy the model
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = factor(term, levels = term)) %>%   # <-- LOCK ORDER
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age",
    str_detect(term, "Gender") ~ "Gender",
    str_detect(term, "social_grade") ~ "Social Grade",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity",
    str_detect(term, "marital_status") ~ "Marital Status",
    str_detect(term, "house_tenure") ~ "Housing Tenure",
    str_detect(term, "working_status") ~ "Working Status",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian",
    str_detect(term, "children_in_household") ~ "Number of Children in Household",
    TRUE ~ "Other"
  )) %>%
  # 3. STRICTLY ORDER THE GROUPS
  # We use fct_relevel to define the top-to-bottom order you requested
  mutate(group = fct_relevel(group, 
                             "Age", "Gender", "Social Grade", "Ethnicity", 
                             "Marital Status", "Housing Tenure", "Working Status", 
                             "Parent/Guardian", "Number of Children in Household")) %>%
  # 4. ORDER THE ROWS WITHIN THE GROUPS
  # We arrange by the group level, then by the estimate
  # Create the factor levels for 'term' based on this specific sorted order
  mutate(term = factor(term, levels = rev(unique(term)))) %>%
  mutate(color = ifelse(estimate > 1, "Increase", "Decrease"))

# 5. Forest plot
ggplot(posterior_df, aes(x = term, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "Predictors",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
             legend.position = "none",
        panel.border = element_blank(),
    
    # 2. Add back only the Left (Y) and Bottom (X) lines
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_blank(),        # Removes the little lines
    #     axis.text.y = element_text(size = 10),
    # # Increase the size of the numbers on the bottom axis
    # axis.text.x = element_text(size = 10),
          aspect.ratio = 1.4,
    axis.text.y = element_text(size = 10,  color = "black"),
    # Bold the Odds Ratio numbers (Bottom) - ONLY ONE INSTANCE HERE
    axis.text.x = element_text(size = 10,  color = "black")
    # Bold the Axis Titles
    # axis.title.x = element_text(face = "bold"),
    # axis.title.y = element_text(face = "bold")
    )+
  scale_x_discrete(
  limits = rev(unname(plot_labels)),   # enforce full order including headers
  labels = plot_labels_rev
)
```




## Concerned about negative side effects


```{r vacc_concerned-fits, fig.height=10, message=FALSE, warning=FALSE}

dat_concerned$house_tenure <- fct_collapse(dat_concerned$house_tenure,
  "Own" = c("Own outright", "Own with a mortgage", "Shared ownership scheme"),
  "Missing" = "blank"
)
levels(dat_concerned$marital_status)[levels(dat_concerned$marital_status) == "blank"] <- "Missing"

fit_rstanarm <- stan_glm(
  concerned ~ Age + Gender + social_grade + ethnicity_grp +
    marital_status + house_tenure + working_status +
    parent_guardian + children_in_household,
  
  data = dat_concerned,
  family = binomial(link = "logit"),
      prior = normal(location = 0, scale = 1, autoscale = FALSE),
  weights = weight,
  
  # prior = normal(location = 0, scale = 100, autoscale = FALSE),
  # prior_intercept = normal(location = 0, scale = 100, autoscale = FALSE),
  
  chains = 4,
  iter = 2000,
  seed = 123
)

y_rep <- posterior_predict(fit_rstanarm)
ppc_stat(y = dat_concerned$concerned, yrep = y_rep[1:4000, ], stat = "mean")


predictors <- c("Age", "Gender", "social_grade", "ethnicity_grp", 
                "marital_status", "house_tenure", "working_status", 
                "parent_guardian", "children_in_household")

eff_df_bayesian <- map_dfr(predictors, function(p) {
  
  # 1. Create the grid for this specific predictor
  nd <- dat_concerned %>%
    modelr::data_grid(!!sym(p), .model = dat_concerned)
  
  
  # 2. Get the draws on the probability scale
  post_probs <- posterior_epred(fit_rstanarm, newdata = nd, re_formula = NULL)
  
  # 3. Calculate the proportion of draws >= 0.5 for each level
  # colMeans on a logical comparison gives the probability (0 to 1)
  p_gt_50 <- colMeans(post_probs >= 0.5)
  lower_vals <- apply(post_probs, 2, quantile, probs = 0.025)
  upper_vals <- apply(post_probs, 2, quantile, probs = 0.975)
  # 4. Summary statistics
  nd %>%
    mutate(
      predictor = p,
      predictor_level = as.character(!!sym(p)),
      fit = colMeans(post_probs),
      lower = apply(post_probs, 2, quantile, probs = 0.025),
      upper = apply(post_probs, 2, quantile, probs = 0.975),
      # New column: 1 if more than half the posterior mass is >= 0.5, else 0
      # Or simply keep it as a continuous probability if you prefer
      #above_50_threshold = ifelse(p_gt_50 >= 0.5, 1, 0) 
      above_50_threshold = case_when(
        p_gt_50 < 0.5                       ~ 0,
        p_gt_50 >= 0.5 & lower_vals <= 0.5  ~ 1,
        p_gt_50 >= 0.5 & lower_vals > 0.5   ~ 2
      )
    ) %>%
    select(predictor, predictor_level, fit, lower, upper, above_50_threshold)
})

eff_df_bayesian <- eff_df_bayesian %>%
  mutate(threshold_group = case_when(
    above_50_threshold == 2 ~ "Above C.I. no overlap 50%",
    above_50_threshold == 1 ~ "Above C.I. overlap 50%",
    above_50_threshold == 0 ~ "Below C.I. overlap 50%"
  ))


# 1. Update your nice_names to include line breaks for the long ones
nice_names <- c(
  "Age" = "Age",
  "children_in_household" = "Children\nin HH",
  "ethnicity_grp" = "Ethnicity",
  "Gender" = "Gender",
  "house_tenure" = "Housing",
  "marital_status" = "Marital\nStatus",
  "parent_guardian" = "Parental\nStatus",
  "social_grade" = "Social\nGrade",
  "working_status" = "Work\nStatus"
)

# 2. Run the plot with the labeller
ggplot(eff_df_bayesian, aes(x = predictor_level, y = fit, color = threshold_group)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "blue", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  
  scale_color_manual(values = c("Above C.I. no overlap 50%" = "green", 
                                "Above C.I. overlap 50%" = "grey", 
                                "Below C.I. overlap 50%" = "red")) + 
  
  # Use the 'labeller' argument to map the raw names to your nice names
  facet_grid(~ predictor, 
             scales = "free_x", 
             space = "free_x", 
             labeller = as_labeller(nice_names)) + 
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_blank(),           
    strip.text = element_text(face = "bold", size = 11, lineheight = 0.9), 
    panel.spacing = unit(0.5, "lines") # Increased slightly from 0 to avoid text overlap
  ) +
  labs(
    y = "Probability concerned on negative side effects",
    x = "Predictor Level",
    color = "Probability Threshold",
    title = "Posterior Predictive Probabilities"
  )

```

```{r vacc_concerned_table, message=FALSE, warning=FALSE}
broom::tidy(fit_rstanarm, conf.int = TRUE) |> 
  kable(digits = 3, caption = "Logistic Regression Results") %>%
  kable_styling(full_width = FALSE)

library(rstanarm)
library(broom.mixed)
library(knitr)
library(kableExtra)
tab_latex <- broom::tidy(
  fit_rstanarm,
  conf.int = TRUE,
  # conf.level = 0.95,
  # conf.method = "quantile",
  exponentiate = FALSE   # remove if you want log-odds
)

latex_table <- kable(
  tab_latex,
  format = "latex",
  booktabs = TRUE,
  digits = 3,
  caption = "Bayesian Logistic Regression Results (Odds Ratios, 95\\% Credible Intervals)",
  label = "tab:bayes_logit"
)

cat(latex_table)


```

```{r}

library(tidyverse)
library(broom.mixed)

# 1. Process data with strict categorical ordering
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term != "(Intercept)") %>%
  # Define the categorical order you requested
  mutate(group_order = case_when(
    str_detect(term, "Age") ~ 1,
    str_detect(term, "Gender") ~ 2,
    str_detect(term, "social_grade") ~ 3,
    str_detect(term, "ethnicity_grp") ~ 4,
    str_detect(term, "marital_status") ~ 5,
    str_detect(term, "house_tenure") ~ 6,
    str_detect(term, "working_status") ~ 7,
    str_detect(term, "parent_guardian") ~ 8,
    str_detect(term, "children_in_household") ~ 9,
    TRUE ~ 10
  )) %>%
  # Arrange by the group order index, then by estimate within groups if desired
  arrange(group_order, estimate) %>%
  # Use rev() because ggplot plots factor levels from bottom to top on the y-axis
  mutate(term_label = factor(term, levels = rev(unique(term))),
         color = ifelse(estimate > 1, "Increase", "Decrease"))

# 2. Forest plot
ggplot(posterior_df, aes(x = term_label, y = estimate, color = color)) +
  # Reference line at 1 for Odds Ratios
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_minimal(base_size = 14)
```


```{r}
library(tidyverse)
library(broom.mixed)

# 1. Get the raw results from rstanarm
# Changed 'prob' to 'conf.level'
results <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE, conf.level = 0.95) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    # Approximate p-value from Z-score (Standard for academic tables)
    p.value = 2 * (1 - pnorm(abs(estimate / std.error))), 
    OR = sprintf("%.2f", estimate),
    CI = sprintf("%.2f, %.2f", conf.low, conf.high),
    P = case_when(
      p.value < 0.001 ~ "<0.001",
      p.value >= 0.99 ~ ">0.99",
      TRUE ~ sprintf("%.3f", p.value)
    )
  )


clean_table <- results %>%
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age (ref: 18-24)",
    str_detect(term, "Gender") ~ "Gender (ref: Female)",
    str_detect(term, "social_grade") ~ "Social Grade (ref: High)",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity (ref: White)",
    str_detect(term, "marital_status") ~ "Marital Status (ref: Married/ Civil Partnership)",
    str_detect(term, "house_tenure") ~ "Housing Tenure (ref: Own)",
    str_detect(term, "working_status") ~ "Working Status (ref: Working full-time)",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian of Child Aged (ref: 4 years and under)",
    str_detect(term, "children_in_household") ~ "Number of Children in Household (ref: 0)",
    TRUE ~ "Other"
  )) %>%
  # This regex removes the variable name prefix to leave just the level name
  mutate(level_name = str_remove(term, "Age|Gender|social_grade|ethnicity_grp|marital_status|house_tenure|working_status|parent_guardian|children_in_household"))

group_order <- c("Age (ref: 18-24)", "Gender (ref: Female)", "Social Grade (ref: High)", 
                 "Ethnicity (ref: White)", "Marital Status (ref: Married/ Civil Partnership)", 
                 "Housing Tenure (ref: Own)", "Working Status (ref: Working full-time)", 
                 "Parent/Guardian of Child Aged (ref: 4 years and under)", "Number of Children in Household (ref: 0)")

cat("% Copy the lines below into your LaTeX tabular environment\n")
for(g in group_order) {
  # Print the Header Row
  cat(paste0(g, " &  &  &  \\\\ \n"))
  cat("\\addlinespace[2.5pt]\n") # Adds the space you had in your template
  
  # Filter and print the indented sub-rows
  sub_grp <- clean_table %>% filter(group == g)
  
  if(nrow(sub_grp) > 0) {
    for(i in 1:nrow(sub_grp)) {
      # Use quadruple backslashes to result in two backslashes in the output
      cat(paste0("\\;\\;\\;\\;", sub_grp$level_name[i], " & ", 
                 sub_grp$OR[i], " & ", sub_grp$CI[i], " & ", sub_grp$P[i], " \\\\ \n"))
    }
  }
}

```

```{r}

# plot_labels <- c(
#   "25-34",
#   "35-44",
#   "45-54", 
#   "≥55",
#   "Male",
#   "Low",
#   "Asian",
#   "Black",
#   "Mixed",
#   "Other",
#   "Prefer not to say",
#   "Living as married",
#   "Never Married",
#   "Separated/ Divorced",
#   "Widowed",
#   "blank",
#   "Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "Rent-free" = "house_tenureRent-free",
#   "Rent from a housing association",
#   "Rent from a private landlord",
#   "Rent from my local authority",
#   "Family/ friends but pay rent",
#   "Shared ownership scheme",
#   "Other",
#   "blank",
#   "Working part time",
#   "Full time student",
#   "Not working/ Other",
#   "Retired",
#   "Unemployed",
#   "5 to 11 years",
#   "12 to 16 years",
#   "17 to 18 years",
#   "Over 18 years",
#   "Not parent/ guardian",
#   "1",
#   "2",
#   "≥3",
#   "Refused"
# )
# 
# plot_labels <- c(
#   "Age (ref: 18-24)" = "header_age",
#   "   25-34" = "Age25-34",
#   "   35-44" = "Age35-44",
#   "   45-54" = "Age45-54",
#   "   ≥ 55" = "Age55+",
#   "Gender (ref: Female)" = "header_gender",
#   "   Male" = "GenderMale",
#   "Social Grade (ref: High)" = "header_social",
#   "   Low" = "social_gradeLow",
#   "Ethnicity (ref: White)" = "header_eth",
#   "   Asian" = "ethnicity_grpAsian",
#   "   Black" = "ethnicity_grpBlack",
#   "   Mixed" = "ethnicity_grpMixed",
#   "   Other" = "ethnicity_grpOther",
#   "   Prefer not to say" = "ethnicity_grpPrefer not to say",
#   "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
#   "   Living as married" = "marital_statusLiving as married",
#   "   Never Married" = "marital_statusNever Married",
#   "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
#   "   Widowed" = "marital_statusWidowed",
#   "   blank" = "marital_statusblank",
#   "Housing Tenure (ref: Own outright)" = "header_housing",
#   "   Own with a mortgage" = "house_tenureOwn with a mortgage",
#   "   Rent-free" = "house_tenureRent-free",
#   "   Rent from a housing association" = "house_tenureRent from a housing association",
#   "   Rent from a private landlord" = "house_tenureRent from a private landlord",
#   "   Rent from my local authority" = "house_tenureRent from my local authority",
#   "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
#   "   Shared ownership scheme" = "house_tenureShared ownership scheme",
#   "   Other" = "house_tenureOther",
#   "   blank" = "house_tenureblank",
#   "Working Status (ref: Working full time)" = "header_work",
#   "   Working part time" = "working_statusWorking part time",
#   "   Full time student" = "working_statusFull time student",
#   "   Not working/ Other" = "working_statusNot working/ Other",
#   "   Retired" = "working_statusRetired",
#   "   Unemployed" = "working_statusUnemployed",
#   "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
#   "   5 to 11 years" = "parent_guardian5 to 11 years",
#   "   12 to 16 years" = "parent_guardian12 to 16 years",
#   "   17 to 18 years" = "parent_guardian17 to 18 years",
#   "   Over 18 years" = "parent_guardianOver 18 years",
#   "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
#   "Children in Household (ref: 0)" = "header_children",
#   "   1" = "children_in_household1",
#   "   2" = "children_in_household2",
#   "   ≥ 3" = "children_in_household3+",
#   "   Refused" = "children_in_householdRefused"
# )
# 
# plot_labels_rev <- setNames(names(plot_labels), plot_labels)

plot_labels <- c(
  "25-34",
  "35-44",
  "45-54", 
  "≥55",
  "Male",
  "Low",
  "Asian",
  "Black",
  "Mixed",
  "Other",
  "Prefer not to say",
  "Living as married",
  "Never Married",
  "Separated/ Divorced",
  "Widowed",
  "Missing",
  "Rent-free" = "house_tenureRent-free",
  "Rent from a housing association",
  "Rent from a private landlord",
  "Rent from my local authority",
  "Family/ friends but pay rent",
  "Other",
  "Missing",
  "Working part-time",
  "Full-time student",
  "Not working/ Other",
  "Retired",
  "Unemployed",
  "5 to 11 years",
  "12 to 16 years",
  "17 to 18 years",
  "Over 18 years",
  "Not parent/ guardian",
  "1",
  "2",
  "≥3",
  "Refused"
)

plot_labels <- c(
  "Age (ref: 18-24)" = "header_age",
  "   25-34" = "Age25-34",
  "   35-44" = "Age35-44",
  "   45-54" = "Age45-54",
  "   ≥ 55" = "Age55+",
  "Gender (ref: Female)" = "header_gender",
  "   Male" = "GenderMale",
  "Social Grade (ref: High)" = "header_social",
  "   Low" = "social_gradeLow",
  "Ethnicity (ref: White)" = "header_eth",
  "   Asian" = "ethnicity_grpAsian",
  "   Black" = "ethnicity_grpBlack",
  "   Mixed" = "ethnicity_grpMixed",
  "   Other" = "ethnicity_grpOther",
  "   Prefer not to say" = "ethnicity_grpPrefer not to say",
  "Marital Status (ref: Married/ Civil Partnership)" = "header_marital",
  "   Living as married" = "marital_statusLiving as married",
  "   Never Married" = "marital_statusNever Married",
  "   Separated/ Divorced" = "marital_statusSeparated/ Divorced",
  "   Widowed" = "marital_statusWidowed",
  "   Missing" = "marital_statusMissing",
  "Housing Tenure (ref: Own)" = "header_housing",
  "   Rent-free" = "house_tenureRent-free",
  "   Rent from a housing association" = "house_tenureRent from a housing association",
  "   Rent from a private landlord" = "house_tenureRent from a private landlord",
  "   Rent from my local authority" = "house_tenureRent from my local authority",
  "   Family/ friends but pay rent" = "house_tenureFamily/ friends but pay rent",
  "   Other" = "house_tenureOther",
  "   Missing" = "house_tenureMissing",
  "Working Status (ref: Working full-time)" = "header_work",
  "   Working part-time" = "working_statusWorking part time",
  "   Full-time student" = "working_statusFull time student",
  "   Not working/ Other" = "working_statusNot working/ Other",
  "   Retired" = "working_statusRetired",
  "   Unemployed" = "working_statusUnemployed",
  "Parent/Guardian of Child Aged (ref: 4 years and under)" = "header_parent",
  "   5 to 11 years" = "parent_guardian5 to 11 years",
  "   12 to 16 years" = "parent_guardian12 to 16 years",
  "   17 to 18 years" = "parent_guardian17 to 18 years",
  "   Over 18 years" = "parent_guardianOver 18 years",
  "   Not parent/ guardian" = "parent_guardianNot parent/ guardian",
  "Number of Children in Household (ref: 0)" = "header_children",
  "   1" = "children_in_household1",
  "   2" = "children_in_household2",
  "   ≥ 3" = "children_in_household3+",
  "   Refused" = "children_in_householdRefused"
)

plot_labels_rev <- setNames(names(plot_labels), plot_labels)




```



```{r}


library(tidyverse)
library(broom.mixed)

# 1. Tidy the model
posterior_df <- tidy(fit_rstanarm, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = factor(term, levels = term)) %>%   # <-- LOCK ORDER
  mutate(group = case_when(
    str_detect(term, "Age") ~ "Age",
    str_detect(term, "Gender") ~ "Gender",
    str_detect(term, "social_grade") ~ "Social Grade",
    str_detect(term, "ethnicity_grp") ~ "Ethnicity",
    str_detect(term, "marital_status") ~ "Marital Status",
    str_detect(term, "house_tenure") ~ "Housing Tenure",
    str_detect(term, "working_status") ~ "Working Status",
    str_detect(term, "parent_guardian") ~ "Parent/Guardian",
    str_detect(term, "children_in_household") ~ "Number of Children in Household",
    TRUE ~ "Other"
  )) %>%
  # 3. STRICTLY ORDER THE GROUPS
  # We use fct_relevel to define the top-to-bottom order you requested
  mutate(group = fct_relevel(group, 
                             "Age", "Gender", "Social Grade", "Ethnicity", 
                             "Marital Status", "Housing Tenure", "Working Status", 
                             "Parent/Guardian", "Number of Children in Household")) %>%
  # 4. ORDER THE ROWS WITHIN THE GROUPS
  # We arrange by the group level, then by the estimate
  # Create the factor levels for 'term' based on this specific sorted order
  mutate(term = factor(term, levels = rev(unique(term)))) %>%
  mutate(color = ifelse(estimate > 1, "Increase", "Decrease"))

# 5. Forest plot
ggplot(posterior_df, aes(x = term, y = estimate, color = color)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = c("Increase" = "blue", "Decrease" = "red")) +
  labs(
    x = "Predictors",
    y = "Odds Ratio (95% Credible Interval)",
    color = "Effect"
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        legend.position = "none",
        panel.border = element_blank(),
    
    # 2. Add back only the Left (Y) and Bottom (X) lines
    axis.line = element_line(color = "black", linewidth = 0.5),
    #     axis.text.y = element_text(size = 10),
    # # Increase the size of the numbers on the bottom axis
    # axis.text.x = element_text(size = 10),
          aspect.ratio = 1.4,
    axis.ticks = element_blank(),
    axis.text.y = element_text(size = 10, color = "black"),
    # Bold the Odds Ratio numbers (Bottom) - ONLY ONE INSTANCE HERE
    axis.text.x = element_text(size = 10, color = "black")
    # Bold the Axis Titles
    # axis.title.x = element_text(face = "bold"),
    # axis.title.y = element_text(face = "bold")
    )+
  scale_x_discrete(
  limits = rev(unname(plot_labels)),   # enforce full order including headers
  labels = plot_labels_rev
)
```




<!-- ## Childhood vaccines are important for a child's health -->

<!-- ```{r vacc_important-fits, fig.height=10, message=FALSE, warning=FALSE} -->
<!-- form_full <-  -->
<!--   "vacc_important ~ Age + Gender + social_grade + ethnicity_grp + marital_status + working_status + parent_guardian18 + children_in_household" -->
<!--   # "vacc_important ~ Age + Gender + social_grade + ethnicity_grp + marital_status + working_status + parent_guardian + children_in_household" -->
<!--   # "vacc_important ~ Age + Gender + social_grade + ethnicity_grp + marital_status + house_tenure + working_status + parent_guardian + children_in_household" -->

<!-- fit <-  -->
<!--   dat_vacc_imp |>  -->
<!--   filter(marital_status != "blank") |>  -->
<!--   glm(form_full, data = _, -->
<!--       family = binomial(link = "logit"), -->
<!--        weights = weight) -->
<!-- ``` -->

<!-- ```{r vacc_important_table, message=FALSE, warning=FALSE} -->
<!-- broom::tidy(fit, conf.int = TRUE) |>  -->
<!--   kable(digits = 3, caption = "Logistic Regression Results") %>% -->
<!--   kable_styling(full_width = FALSE) -->
<!-- ``` -->

<!-- ```{r vacc_important-plot-effects, fig.height=10, fig.width=10, fig.path="figures/", dev="png", message=FALSE, warning=FALSE} -->
<!-- # plot(allEffects(fit)) -->

<!-- vacc_imp_list <- as.data.frame(allEffects(fit)) -->

<!-- # Convert to list of data frames with a consistent column name -->
<!-- vacc_imp_df <- -->
<!--   purrr::map(names(vacc_imp_list), function(varname) { -->
<!--     df <- as.data.frame(vacc_imp_list[[varname]]) -->
<!--     colnames(df)[1] <- "predictor_level" -->
<!--     df$predictor <- varname -->
<!--     df -->
<!--   }) |>  -->
<!--   bind_rows() -->

<!-- mean_predicted_prob <- mean(vacc_imp_df$fit, na.rm = TRUE) -->

<!-- vacc_imp_df <- vacc_imp_df |> -->
<!--   mutate(signif = case_when( -->
<!--     upper < mean_predicted_prob ~ "Below", -->
<!--     fit < mean_predicted_prob ~ "below_overlap", -->
<!--     lower > mean_predicted_prob ~ "Above", -->
<!--     TRUE                        ~ "Overlapping" -->
<!--   )) -->

<!-- vacc_imp_aggregate <-  -->
<!--   vacc_imp_aggregate |>  -->
<!--   rename(fit = p_vacc_important) -->

<!-- ggplot(vacc_imp_df, aes(x = predictor_level, y = fit, color = signif)) + -->
<!--   geom_hline(aes(yintercept = mean_predicted_prob), linetype = "dashed", color = "blue", linewidth = 1) + -->
<!--   geom_point() + -->
<!--   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) + -->
<!--   # Manually set the colors (this part is still needed to color the points) -->
<!--   scale_color_manual(values = c("Above" = "green",  -->
<!--                                 "Below" = "red",  -->
<!--                                 "Overlapping" = "grey50",  -->
<!--                                 below_overlap = "orange")) + -->
<!--   theme_minimal() + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   facet_grid(~ predictor, scales = "free_x", drop = TRUE) + -->
<!--   ylab("Probability think childhood vaccines are important for a child's health") + -->
<!--   # raw data aggregated values -->
<!--   geom_point(data = vacc_imp_aggregate, color = "black", pch = 1, stroke = 1.5) -->
<!-- ``` -->

<!-- ```{r vacc_important-lor-dwplot-wave1, eval=FALSE, message=FALSE, warning=FALSE} -->
<!-- fit |>  -->
<!--   tidy(conf.int = TRUE) |>  -->
<!--   dwplot() + -->
<!--   theme_minimal() + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   coord_flip() + -->
<!--   theme(legend.position = "none") + -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   xlab("Log-odds ratio for think childhood vaccines are important for a child's health") -->
<!-- ``` -->

<!-- ```{r vacc_important-lor-forest-plot, fig.height=10, fig.width=10, fig.path="figures/", dev="png", message=FALSE, warning=FALSE} -->
<!-- coef_df <- tidy(fit, conf.int = TRUE) |> -->
<!--   filter(term != "(Intercept)") # don't plot intercept -->

<!-- row_vars <- c("Age", "Gender", "ethnicity_grp", "social_grade", "marital_status",  -->
<!--               "house_tenure", "working_status", "parent_guardian", "children_in_household") -->

<!-- variable_pattern <- paste(row_vars, collapse = "|") -->

<!-- # split the 'term' column -->
<!-- coef_df <- coef_df |> -->
<!--   extract( -->
<!--     col = term, -->
<!--     into = c("variable", "level"), -->
<!--     regex = paste0("(", variable_pattern, ")(.*)"), -->
<!--     remove = FALSE  # Optional: Keep the original 'term' column -->
<!--   ) -->

<!-- coef_df <- coef_df |> -->
<!--   mutate(significance = case_when( -->
<!--     conf.low > 0 ~ "Positive", -->
<!--     conf.high < 0 ~ "Negative", -->
<!--     TRUE ~ "Not Significant" -->
<!--   )) -->

<!-- ggplot(coef_df, aes(x = level, y = estimate, color = significance)) + -->
<!--   geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", linewidth = 1) + -->
<!--   geom_point(size = 3) + -->
<!--   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) + -->
<!--   facet_grid(~variable, scales = "free_x", space = "free_x") + -->
<!--   scale_color_manual( -->
<!--     name = "Effect Direction", -->
<!--     values = c( -->
<!--       "Positive" = "#1a9641", -->
<!--       "Negative" = "#d7191c", -->
<!--       "Not Significant" = "grey30" -->
<!--     ) -->
<!--   ) + -->
<!--   theme_minimal(base_size = 12) + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   labs( -->
<!--     x = "Category", -->
<!--     y = "Log-odds ratio for think childhood vaccines are important for a child's health" -->
<!--   ) -->
<!-- ``` -->

<!-- ## Heard (positive) about campaign -->

<!-- ```{r campaign_hear-fits, fig.height=10, message=FALSE, warning=FALSE} -->
<!-- form_full <-  -->
<!--   "campaign_hear ~ Age + Gender + social_grade + ethnicity_grp + marital_status + house_tenure + working_status + parent_guardian + children_in_household" -->

<!-- fit <- glm(form_full, data = dat_hear,  -->
<!--            family = binomial(link = "logit"), -->
<!--             weights = weight) -->
<!-- ``` -->

<!-- ```{r campaign_hear_table, message=FALSE, warning=FALSE} -->
<!-- broom::tidy(fit, conf.int = TRUE) |>  -->
<!--   kable(digits = 3, caption = "Logistic Regression Results") %>% -->
<!--   kable_styling(full_width = FALSE) -->
<!-- ``` -->

<!-- ```{r campaign_hear-plot-effects, fig.height=10, fig.width=10, fig.path="figures/", dev="png", message=FALSE, warning=FALSE} -->
<!-- hear_list <- as.data.frame(allEffects(fit)) -->

<!-- # Convert to list of data frames with a consistent column name -->
<!-- hear_df <- -->
<!--   purrr::map(names(hear_list), function(varname) { -->
<!--     df <- as.data.frame(hear_list[[varname]]) -->
<!--     colnames(df)[1] <- "predictor_level" -->
<!--     df$predictor <- varname -->
<!--     df -->
<!--   }) |>  -->
<!--   bind_rows() -->

<!-- mean_predicted_prob <- mean(hear_df$fit, na.rm = TRUE) -->

<!-- hear_df <- hear_df |> -->
<!--   mutate(signif = case_when( -->
<!--     upper < mean_predicted_prob ~ "Below", -->
<!--     fit < mean_predicted_prob ~ "below_overlap", -->
<!--     lower > mean_predicted_prob ~ "Above", -->
<!--     TRUE                        ~ "Overlapping" -->
<!--   )) -->

<!-- hear_aggregate <-  -->
<!--   hear_aggregate |>  -->
<!--   rename(fit = p_campaign_hear) -->

<!-- ggplot(hear_df, aes(x = predictor_level, y = fit, color = signif)) + -->
<!--   geom_hline(aes(yintercept = mean_predicted_prob), linetype = "dashed", color = "blue", linewidth = 1) + -->
<!--   geom_point() + -->
<!--   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) + -->
<!--   # Manually set the colors (this part is still needed to colour the points) -->
<!--   scale_color_manual(values = c("Above" = "green",  -->
<!--                                 "Below" = "red",  -->
<!--                                 "Overlapping" = "grey50",  -->
<!--                                 below_overlap = "orange")) + -->
<!--   theme_minimal() + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   facet_grid(~ predictor, scales = "free_x", drop = TRUE) + -->
<!--   ylab("Probability heard (positive) about campaign") + -->
<!--   # raw data aggregated values -->
<!--   geom_point(data = hear_aggregate, color = "black", pch = 1, stroke = 1.5) -->
<!-- ``` -->

<!-- ```{r eval=FALSE, message=FALSE, warning=FALSE} -->
<!-- fit |>  -->
<!--   tidy(conf.int = TRUE) |>  -->
<!--   dwplot() + -->
<!--   theme_minimal() + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   coord_flip() + -->
<!--   theme(legend.position = "none") + -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   xlab("Log-odds ratio for heard (positive) about campaign") -->
<!-- ``` -->

<!-- ```{r campaign_hear-lor-forest-plot, fig.height=10, fig.width=10, fig.path="figures/", dev="png", message=FALSE, warning=FALSE} -->
<!-- coef_df <- tidy(fit, conf.int = TRUE) |> -->
<!--   filter(term != "(Intercept)") # don't plot intercept -->

<!-- row_vars <- c("Age", "Gender", "ethnicity_grp", "social_grade", "marital_status",  -->
<!--               "house_tenure", "working_status", "parent_guardian", "children_in_household") -->

<!-- variable_pattern <- paste(row_vars, collapse = "|") -->

<!-- # split the 'term' column -->
<!-- coef_df <- coef_df |> -->
<!--   extract( -->
<!--     col = term, -->
<!--     into = c("variable", "level"), -->
<!--     regex = paste0("(", variable_pattern, ")(.*)"), -->
<!--     remove = FALSE  # Optional: Keep the original 'term' column -->
<!--   ) -->

<!-- coef_df <- coef_df |> -->
<!--   mutate(significance = case_when( -->
<!--     conf.low > 0 ~ "Positive", -->
<!--     conf.high < 0 ~ "Negative", -->
<!--     TRUE ~ "Not Significant" -->
<!--   )) -->

<!-- ggplot(coef_df, aes(x = level, y = estimate, color = significance)) + -->
<!--   geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", linewidth = 1) + -->
<!--   geom_point(size = 3) + -->
<!--   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) + -->
<!--   facet_grid(~variable, scales = "free_x", space = "free_x") + -->
<!--   scale_color_manual( -->
<!--     name = "Effect Direction", -->
<!--     values = c( -->
<!--       "Positive" = "#1a9641", -->
<!--       "Negative" = "#d7191c", -->
<!--       "Not Significant" = "grey30" -->
<!--     ) -->
<!--   ) + -->
<!--   theme_minimal(base_size = 12) + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   labs( -->
<!--     x = "Category", -->
<!--     y = "Log-odds ratio for heard (positive) about campaign" -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r generate-html, eval=FALSE, echo=FALSE} -->
<!-- rmarkdown::render(here::here("scripts/analysis.Rmd"), output_format = "html_document") -->
<!-- ``` -->
